---
layout: single
title: "Reproducibility Guide: RoBMA Re-analysis of Singleton et al. (2026)"
output:
  md_document:
    variant: markdown_github
    preserve_yaml: true
---

This document provides a complete reproducibility guide for the Robust Bayesian
Meta-Analysis (RoBMA) re-analysis of Singleton et al. (2026), submitted as a
Matters Arising to *Nature Mental Health*.

**Target paper:** Singleton, S. P. et al. A living systematic review,
meta-analysis and open-data resource of randomized controlled trials of
psilocybin treatment for symptoms of depression. *Nature Mental Health*
**4**, 870–880 (2026). https://doi.org/10.1038/s44220-026-00630-8.

**Important — published paper, not the medRxiv preprint.** An earlier version
of this document was accidentally anchored to Singleton et al.'s medRxiv
preprint (posted August 2025), not the peer-reviewed, published version above.
Between preprint and publication the primary model grew from 9 to 12 studies
(3 more RCTs were added: Lewis 2025, Luquiens 2025, Ross 2025) and the
database grew from 12 to 15 studies total. Every number in this document is
computed against the **published** paper's own dataset version and study
composition — do not re-introduce the preprint's numbers.

**Dataset:** Openly available via `metapsyData::getData("depression-psiloctr", version = "25.1.2")`.
Version pinned to match the exact version cited in the published paper's own
reference list ("Version 25.1.2", doi:10.5281/zenodo.15714852). Verified
directly against the paper (`natmh2026.pdf`): this version's raw pull
reproduces their reported 15-study database (Table 1) and their 12-study
primary model exactly (same study list, same Hedges' g = −0.90 [−1.26, −0.55],
tau2 = 0.12, n = 585 — matches to the decimal). Do not omit the version
argument — `metapsyData` is a living database and defaults to "latest," which
will keep growing as new trials are added.

The analysis applies RoBMA (Maier, Bartoš & Wagenmakers, 2022, *Psychological
Methods*) to the same dataset used by Singleton et al. RoBMA was not used in
the original paper, which assessed publication bias using only Egger's test
on their primary model and funnel plot inspection (both non-significant; see
the live-recomputed Egger's test below for exact statistics — this document
never hardcodes numbers from the published paper).

Full source code is maintained at: [github.com/metapsy-project/data-depression-psiloctr](https://github.com/metapsy-project/data-depression-psiloctr)

---

## Computational note

RoBMA fits 12 MCMC models per call. Running all 17 analyses from scratch takes
approximately 45–90 minutes depending on hardware. Set `run_fresh <- TRUE` in
the setup chunk to recompute; leave as `FALSE` to load pre-computed results from
`psilodep-robma-results.RData`.

```{r setup, include=FALSE}
run_fresh <- FALSE   # set TRUE to recompute all RoBMA models from scratch

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

---

## Overview

### What RoBMA adds

Singleton et al. (2026) assessed publication bias via Egger's test and funnel
plot inspection, finding no significant asymmetry on their primary model
(exact statistics recomputed live below, not transcribed from the paper).
However, Egger's test has limited power at this sample size and provides no
bias-corrected effect estimate.

RoBMA addresses both gaps by fitting an ensemble of 12 models that jointly vary
across three dimensions:

1. **Effect** — H₀: μ = 0 vs H₁: μ > 0 (Cauchy prior, scale = 0.707)
2. **Heterogeneity** — fixed (τ = 0) vs random (InvGamma(1, 0.15))
3. **Publication bias** — no bias vs four Vevea-Hedges step weight function
   models (one-sided at 0.05; one-sided at 0.05/0.10; two-sided at 0.05;
   two-sided at 0.05/0.10) plus PET-PEESE

Model averaging over these 12 models delivers:

- **BF_effect** — Bayes Factor for effect existing vs not
- **BF_het** — Bayes Factor for between-study heterogeneity
- **BF_pb** — Bayes Factor for publication bias
- **Model-averaged posterior** of μ (pooled effect) and τ (heterogeneity SD),
  corrected for publication bias

### Sign convention

`metapsyTools` outputs negative Hedges' g (negative = psilocybin reduces
depression scores relative to control). RoBMA's default PSMA preset uses a
one-sided prior assuming a positive treatment effect. All effect sizes are
**negated** prior to input (positive g = psilocybin beneficial) and results
are reported in this positive convention throughout.

**Justification for directional prior:** All included trials compared psilocybin
against placebo or inactive control; prior research and mechanism provide a clear
directional expectation that psilocybin reduces depression. A one-sided prior is
therefore appropriate. If the true population effect were negative (psilocybin
worse than control), the PSMA prior would be misspecified — this is an assumption
worth noting, not a decision requiring defence.

### Model-averaging vs model selection

RoBMA does **not** select a single best model. It averages posterior estimates
across all 12 models, weighted by each model's posterior probability. The reported
μ and τ are therefore model-averaged quantities: they integrate uncertainty about
whether publication bias exists, whether effects are heterogeneous, and what the
effect size is — simultaneously. This is distinct from choosing the "winning" model
and reporting its estimates, which would understate total uncertainty.

---

## Load Required Packages

```{r packages}
library(RoBMA)          # v4.0.0 — Robust Bayesian Meta-Analysis
library(metapsyData)    # open dataset access
library(metapsyTools)   # data filtering utilities
library(bayesmeta)      # for comparison with Singleton et al.'s Bayesian analysis
library(dmetar)         # Egger's test (for comparison)
library(tidyverse)
library(ggplot2)
library(patchwork)
library(ggplotify)
```

---

## Data Loading and Quality Checks

The dataset is identical to that used by Singleton et al. (2026). We perform
the same quality checks they report.

```{r load-data}
d    <- getData("depression-psiloctr", version = "25.1.2")  # pinned to the published paper's own dataset citation
data <- d$data

checkDataFormat(data)
checkConflicts(data,
  vars.for.id = c("study", "outcome_type", "instrument",
                  "study_time_point", "time_weeks", "rating"))
```

---

## Data Preparation and Filtering

We apply the same filtering decisions as Singleton et al.'s primary analysis.
All seven decisions are documented explicitly.

```{r filter-primary}
# Primary analysis dataset — mirrors data_main in Singleton et al.
# Filter decisions:
#   1. Primary instrument per study (prevents double-counting scales)
#   2. Primary timepoint per study (prevents double-counting follow-ups)
#   3. Exclude post-crossover rows (prevents double-counting crossover phases)
#   4. Endpoint data only (msd = mean/SD; imsd = imputed mean/SD)
#   5. Goodwin 2022: exclude 10 mg arm (keep 25 mg vs placebo only)
#   6. Exclude Krempien 2023 (different design; see Singleton et al. methods)
#   7. Exclude Carhart-Harris 2021 (active comparator, not placebo-controlled)

data_main <- data |>
  filterPoolingData(
    primary_instrument == "1",
    primary_timepoint  == "1",
    is.na(post_crossover) | !Detect(post_crossover, "1"),
    outcome_type == "msd" | outcome_type == "imsd",
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm1)) & Detect(multi_arm1, "10 mg")),
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm2)) & Detect(multi_arm2, "10 mg")),
    !Detect(study, "Krempien 2023"),
    !Detect(study, "Carhart-Harris 2021")
  )

cat("Studies in primary analysis:", n_distinct(data_main$study), "\n")
cat("Studies:", paste(sort(unique(data_main$study)), collapse = ", "), "\n")
```

### Subgroup and sensitivity datasets

```{r filter-subgroups}
# Subgroup analyses
# "Diagnosis of MDD" subgroup. `diagnosis` values in this dataset are
# "mdd"/"trd"/"dep"/"cancer"/"aud". Treatment-resistant depression (trd) is
# clinically MDD-spectrum and is included; "dep" (used for the COVID-19
# -related depression studies, Back 2024 and Lewis 2025 — a distinct
# population per Table 1) is NOT. Verified against every reported statistic
# in the published paper, not just k: diagnosis %in% c("mdd","trd") gives
# k=5 (Davis 2021, Goodwin 2022, Raison 2023, Rosenblat 2024, von Rotz 2023),
# n=358, g=-0.93 [-1.87, 0.01], tau2=0.33 — an exact match to the decimal.
# (Two earlier, wrong attempts: "dep"|"trd" gives the right k on an older,
# smaller dataset by coincidence; "dep"|"mdd" gives the right k here but the
# wrong g/n, because it swaps in the wrong two studies.)
data_dep <- data_main |>
  filterPoolingData(diagnosis == "mdd" | diagnosis == "trd")

data_excol <- data_main |>
  filterPoolingData(!Detect(blinding, "open-label"))

data_rob <- data_main |>
  filterPoolingData(!Detect(rob, "High"))

data_parallel <- data_main |>
  filterPoolingData(design == "parallel")

data_crossover <- data_main |>
  filterPoolingData(design == "crossover")

# Sensitivity analyses
data_expanded <- data |>
  filterPoolingData(
    primary_instrument == "1",
    primary_timepoint  == "1",
    outcome_type == "msd" | outcome_type == "imsd",
    !(Detect(study, "Goodwin 2022")  & (!is.na(multi_arm1)) & Detect(multi_arm1, "10 mg")),
    !(Detect(study, "Goodwin 2022")  & (!is.na(multi_arm2)) & Detect(multi_arm2, "10 mg")),
    !(Detect(study, "Krempien 2023") & (!is.na(multi_arm1)) & Detect(multi_arm1, "12 mg")),
    !(Detect(study, "Krempien 2023") & (!is.na(multi_arm2)) & Detect(multi_arm2, "12 mg"))
  )

data_outliers <- data_main |>
  filterPoolingData(!Detect(study, "Davis 2021"))

data_g10 <- data |>
  filterPoolingData(
    primary_instrument == "1",
    primary_timepoint  == "1",
    is.na(post_crossover) | !Detect(post_crossover, "1"),
    outcome_type == "msd" | outcome_type == "imsd",
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm1)) & Detect(multi_arm1, "25 mg")),
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm2)) & Detect(multi_arm2, "25 mg")),
    !Detect(study, "Krempien 2023"),
    !Detect(study, "Carhart-Harris 2021")
  )

data_clinician <- data |>
  filterPoolingData(
    primary_timepoint == "1",
    is.na(post_crossover) | !Detect(post_crossover, "1"),
    !(Detect(study, "Goodwin 2022")     & (!is.na(multi_arm1)) & Detect(multi_arm1, "10 mg")),
    !(Detect(study, "Goodwin 2022")     & (!is.na(multi_arm2)) & Detect(multi_arm2, "10 mg")),
    !Detect(study, "Krempien 2023"),
    !Detect(study, "Carhart-Harris 2021"),
    rating == "clinician",
    Detect(instrument_symptom, "depression"),
    outcome_type != "response",
    outcome_type != "remission",
    outcome_type != "change"
  ) |>
  filterPriorityRule(instrument = c("madrs", "grid-ham-d"))

data_selfreport <- data |>
  filterPoolingData(
    primary_timepoint == "1",
    is.na(post_crossover) | !Detect(post_crossover, "1"),
    !(Detect(study, "Goodwin 2022")     & (!is.na(multi_arm1)) & Detect(multi_arm1, "10 mg")),
    !(Detect(study, "Goodwin 2022")     & (!is.na(multi_arm2)) & Detect(multi_arm2, "10 mg")),
    !Detect(study, "Krempien 2023"),
    !Detect(study, "Carhart-Harris 2021"),
    rating == "self-report",
    Detect(instrument_symptom, "depression"),
    outcome_type != "response",
    outcome_type != "remission",
    outcome_type != "change" & outcome_type != "unknown"
  ) |>
  filterPriorityRule(instrument = c("bdi-ii", "bid-1a", "bdi", "qids-sr",
                                    "hads-d", "smdds", "hads"))

# Dichotomous outcome datasets
data_response <- data |>
  filterPoolingData(
    primary_instrument == "1",
    primary_timepoint  == "1",
    outcome_type       == "response",
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm1)) & Detect(multi_arm1, "10 mg")),
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm2)) & Detect(multi_arm2, "10 mg")),
    !Detect(study, "Krempien 2023")
  )

data_remission <- data |>
  filterPoolingData(
    primary_instrument == "1",
    primary_timepoint  == "1",
    outcome_type       == "remission",
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm1)) & Detect(multi_arm1, "10 mg")),
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm2)) & Detect(multi_arm2, "10 mg")),
    !Detect(study, "Krempien 2023")
  )

# Convenience summary
# Multi-timepoint data for multilevel RoBMA — matches the CHE model's
# data_time in Singleton et al.'s own psilodep-meta-analysis.Rmd exactly,
# including their unscoped 10-mg exclusion (applied to all rows, not just
# Goodwin 2022 — verified only Goodwin 2022 has "10 mg" in multi_arm1/2 on
# this pinned dataset, so this is equivalent in effect to scoping it, but
# matching their literal filter here rather than an equivalent-but-different
# one removes any structural ambiguity).
data_time <- data |>
  filterPoolingData(
    is.na(multi_arm1) | !Detect(multi_arm1, "10 mg"),
    is.na(multi_arm2) | !Detect(multi_arm2, "10 mg"),
    !Detect(study, "Krempien 2023"),
    !Detect(study, "Carhart-Harris 2021"),
    primary_instrument == "1",
    time_days > 0,
    is.na(post_crossover) | !Detect(post_crossover, "1"),
    outcome_type == "msd" | outcome_type == "imsd"
  )
cat("data_time: k =", nrow(data_time), "effect sizes from",
    n_distinct(data_time$study), "studies\n")

datasets <- list(
  primary    = data_main,
  dep        = data_dep,
  parallel   = data_parallel,
  crossover  = data_crossover,
  excol      = data_excol,
  rob        = data_rob,
  g10        = data_g10,
  expanded   = data_expanded,
  clinician  = data_clinician,
  selfreport = data_selfreport,
  outliers   = data_outliers
)
purrr::map_int(datasets, \(df) n_distinct(df$study))
```

---

## Helper Functions

```{r helpers}
# Bayes Factor interpretation label (Jeffreys 1961; Kass & Raftery 1995) —
# computed from the value, never asserted as static prose.
bf_label <- function(bf) {
  if (bf < 1)       "favours the null"
  else if (bf < 3)  "anecdotal"
  else if (bf < 10) "moderate"
  else if (bf < 30) "strong"
  else              "very strong / decisive"
}

# Prepare a data_* frame for RoBMA input.
# Negates .g so positive = psilocybin beneficial (required for PSMA prior).
prep_robma <- function(df) {
  df |>
    select(study, .g, .g_se) |>
    filter(!is.na(.g), !is.na(.g_se)) |>
    mutate(g_pos = -.g, g_se = .g_se)
}

# Fit RoBMA with default PSMA preset and study-level effect sizes.
# chains = 3 is RoBMA's package default (verified via args(RoBMA) and against
# the fitted object's fit_control$chains); set explicitly here so the MCMC
# setting reported in the manuscript is pinned in code, not an implicit default.
run_robma <- function(df, seed = 4821, sample = 10000, burnin = 4000, chains = 3) {
  RoBMA(
    yi      = df$g_pos,
    sei     = df$g_se,
    slab    = df$study,
    measure = "SMD",
    seed    = seed,
    sample  = sample,
    burnin  = burnin,
    chains  = chains,
    silent  = TRUE
  )
}

# Extract key quantities from a fitted RoBMA object into a one-row tibble.
extract_robma <- function(fit, label, k, pub_g = NA, pub_lo = NA, pub_hi = NA) {
  s    <- summary(fit)
  comp <- s$inclusion_components
  est  <- s$estimates

  bf_effect <- comp$inclusion_BF[1]
  bf_het    <- comp$inclusion_BF[2]
  bf_pb     <- comp$inclusion_BF[3]
  pp_effect <- comp$post_prob[1]
  pp_pb     <- comp$post_prob[3]

  mu_med  <- est[1, "0.5"]
  mu_lo   <- est[1, "0.025"]
  mu_hi   <- est[1, "0.975"]
  tau_med <- est[2, "0.5"]
  mu_ess  <- est[1, "ESS"]
  mu_rhat <- est[1, "R_hat"]

  tibble(
    Analysis    = label,
    k           = k,
    `Pub. g`    = round(pub_g, 2),
    pub_lo_n    = round(pub_lo, 2),  # numeric, for figure code — never re-type a positional vector
    pub_hi_n    = round(pub_hi, 2),
    `Pub. CI`   = if (!is.na(pub_lo))
                    sprintf("[%.2f, %.2f]", pub_lo, pub_hi)
                  else NA_character_,
    BF_effect   = round(bf_effect, 2),
    PP_effect   = round(pp_effect, 2),
    BF_pb       = round(bf_pb,     2),
    PP_pb       = round(pp_pb,     2),
    mu_median   = round(mu_med,    2),
    mu_lo_n     = round(mu_lo, 2),
    mu_hi_n     = round(mu_hi, 2),
    mu_CrI      = sprintf("[%.2f, %.2f]", mu_lo, mu_hi),
    Attenuation = if (!is.na(pub_g) && pub_g != 0)
                    sprintf("%.0f%%", (1 - mu_med / pub_g) * 100)
                  else NA_character_,
    tau_median  = round(tau_med, 2),
    ESS_mu      = round(mu_ess),
    Rhat_mu     = round(mu_rhat, 3)
  )
}
```

---

## Published Comparator Values — Live Recomputation

**No hardcoded values from the paper.** Every "published" g / RR value used
anywhere in this document is computed here, live, on this same pinned dataset,
using the exact `metapsyTools::runMetaAnalysis` specification from Singleton
et al.'s own reproducibility script (`psilodep-meta-analysis.Rmd`, their
primary/subgroup/sensitivity/CHE/dichotomous chunks). Nothing below is
transcribed from the PDF, a table, or a prior session — every number is
produced by fitting the frequentist model fresh, right now, on the pinned
25.1.2 data. If the pinned version ever changes, these update automatically;
if the paper PDF is wrong, incomplete, or unavailable, this section still
works, because it never reads the paper at all — it re-runs their analysis.

```{r freq-replication}
# Common runMetaAnalysis spec for continuous (g) outcomes — verbatim from
# Singleton et al.'s psilodep-meta-analysis.Rmd (main_results / dep / excol /
# rob / parallel / crossover / expanded / outliers / g10 / clinician /
# selfreport chunks all share this specification).
run_freq_g <- function(df) {
  runMetaAnalysis(df,
    which.run = "overall", es.measure = "g", method.tau = "REML",
    method.tau.ci = "Q-Profile", hakn = TRUE,
    study.var = "study", arm.var.1 = "condition_arm1", arm.var.2 = "condition_arm2",
    measure.var = "instrument", w1.var = "n_arm1", w2.var = "n_arm2",
    time.var = "time_weeks", round.digits = 2)
}

# Common spec for dichotomous (RR) outcomes — verbatim from their
# response/remission chunks.
run_freq_rr <- function(df) {
  runMetaAnalysis(df,
    which.run = "overall", es.measure = "RR", es.type = "raw",
    method.tau = "PM", method.tau.ci = "Q-Profile", hakn = TRUE,
    study.var = "study", arm.var.1 = "condition_arm1", arm.var.2 = "condition_arm2",
    measure.var = "instrument", w1.var = "n_arm1", w2.var = "n_arm2",
    time.var = "time_weeks", round.digits = 2)
}

# Extract g/CI from a metapsyTools continuous result, flipped to this
# document's positive-g convention (metapsyTools reports negative = benefit).
extract_freq_g <- function(res) {
  m <- res$model.overall
  c(g = round(-m$TE.random, 2), lo = round(-m$upper.random, 2), hi = round(-m$lower.random, 2))
}

# Same, but for a fixed-effect (method.tau = "FE") fit — the model object
# stores the fixed-effect estimate under *.fixed, not *.random.
extract_freq_g_fe <- function(res) {
  m <- res$model.overall
  c(g = round(-m$TE.fixed, 2), lo = round(-m$upper.fixed, 2), hi = round(-m$lower.fixed, 2))
}

# Extract RR/CI from a metapsyTools dichotomous result (already on the
# "higher = more response/remission with psilocybin" scale; no sign flip).
extract_freq_rr <- function(res) {
  m <- res$model.overall
  c(g = round(exp(m$TE.random), 2), lo = round(exp(m$lower.random), 2), hi = round(exp(m$upper.random), 2))
}

freq_main        <- run_freq_g(data_main)
freq_expanded    <- run_freq_g(data_expanded)
freq_dep         <- run_freq_g(data_dep)
freq_excol       <- run_freq_g(data_excol)
freq_rob         <- run_freq_g(data_rob)
freq_parallel    <- run_freq_g(data_parallel)
freq_crossover   <- run_freq_g(data_crossover)
freq_g10         <- run_freq_g(data_g10)
freq_clinician   <- run_freq_g(data_clinician)
freq_selfreport  <- run_freq_g(data_selfreport)
freq_outliers    <- run_freq_g(data_outliers)
freq_response    <- run_freq_rr(data_response)
freq_remission   <- run_freq_rr(data_remission)

# Fixed-effect sensitivity — verbatim spec from their `fixed` chunk
# (method.tau <- "FE"; hakn <- FALSE, same data as the primary model). RoBMA
# doesn't need a separate fit for this: BF_het (in the primary model output)
# is itself the fixed-vs-random evidence. This comparator is reported
# alongside the primary RoBMA fit's own BF/mu values, not a new posterior.
freq_fixed <- runMetaAnalysis(data_main,
  which.run = "overall", es.measure = "g", method.tau = "FE",
  method.tau.ci = "Q-Profile", hakn = FALSE,
  study.var = "study", arm.var.1 = "condition_arm1", arm.var.2 = "condition_arm2",
  measure.var = "instrument", w1.var = "n_arm1", w2.var = "n_arm2",
  time.var = "time_weeks", round.digits = 2)

# Individual study effect size (Davis 2021), for the outlier discussion below
# — pulled from the data, not typed in.
davis_g <- -(data_main |> filter(Detect(study, "Davis 2021")) |> pull(.g) |> unique())

# I^2 for the dichotomous fixed-vs-random comparison, checked live rather than
# asserted from the paper.
resp_i2    <- round(freq_response$model.overall$I2 * 100, 1)
remiss_i2  <- round(freq_remission$model.overall$I2 * 100, 1)

# data_main is Singleton et al.'s actual published primary model (12 studies)
# — verified to match their reported g/CI/tau2/n exactly. No separate
# "robustness check" against a different primary is needed anymore.
pub_primary     <- extract_freq_g(freq_main)
pub_expanded    <- extract_freq_g(freq_expanded)    # their "expanded inclusion criteria" sensitivity, k=15
pub_dep         <- extract_freq_g(freq_dep)
pub_excol       <- extract_freq_g(freq_excol)
pub_rob         <- extract_freq_g(freq_rob)
pub_parallel    <- extract_freq_g(freq_parallel)
pub_crossover   <- extract_freq_g(freq_crossover)
pub_g10         <- extract_freq_g(freq_g10)
pub_clinician   <- extract_freq_g(freq_clinician)
pub_selfreport  <- extract_freq_g(freq_selfreport)
pub_outliers    <- extract_freq_g(freq_outliers)
pub_response    <- extract_freq_rr(freq_response)
pub_remission   <- extract_freq_rr(freq_remission)
pub_fixed       <- extract_freq_g_fe(freq_fixed)

# Three-level CHE model — verbatim spec from their `che` chunk, fit on
# data_time (k=37 effect sizes from the same 12 studies as their primary model).
freq_che <- runMetaAnalysis(data_time,
  which.run = "threelevel.che", es.measure = "g", method.tau = "REML",
  method.tau.ci = "Q-Profile", hakn = TRUE,
  study.var = "study", arm.var.1 = "condition_arm1", arm.var.2 = "condition_arm2",
  measure.var = "instrument", w1.var = "n_arm1", w2.var = "n_arm2",
  time.var = "time_days", round.digits = 2)
.che_fit <- freq_che$model.threelevel.che
pub_multilevel <- c(g = round(-as.numeric(.che_fit$b[1]), 2),
                     lo = round(-as.numeric(.che_fit$ci.ub), 2),
                     hi = round(-as.numeric(.che_fit$ci.lb), 2))

# Meta-regression on time since final dose — verbatim spec from their
# `meta-regression` chunk (`metaRegression(time_results$model.threelevel.che,
# ~time_days)`), live on freq_che.
che_timereg <- metaRegression(freq_che$model.threelevel.che, ~time_days)
che_timereg_beta <- round(as.numeric(che_timereg$b[2]), 4)
che_timereg_p    <- round(as.numeric(che_timereg$pval[2]), 3)

# Egger's test on the primary model — live, referenced in the Overview text
# and in the dedicated Egger's-test section below.
egger_primary <- eggers.test(freq_main$model.overall)

results_table_pub_summary <- tibble(
  Analysis = c(sprintf("Primary (k=%d)", n_distinct(data_main$study)),
               sprintf("Expanded inclusion criteria (k=%d)", n_distinct(data_expanded$study)),
               "Diagnosis", "Excl. open-label",
               "Excl. high RoB", "Parallel", "Crossover", "Goodwin 10mg", "Clinician-rated",
               "Self-report", "Excl. Davis 2021", "Response (RR)", "Remission (RR)", "Multilevel CHE"),
  g_or_RR  = c(pub_primary["g"], pub_expanded["g"], pub_dep["g"], pub_excol["g"], pub_rob["g"],
               pub_parallel["g"], pub_crossover["g"], pub_g10["g"], pub_clinician["g"],
               pub_selfreport["g"], pub_outliers["g"], pub_response["g"], pub_remission["g"], pub_multilevel["g"]),
  CI = c(sprintf("[%.2f, %.2f]", pub_primary["lo"], pub_primary["hi"]),
         sprintf("[%.2f, %.2f]", pub_expanded["lo"], pub_expanded["hi"]),
         sprintf("[%.2f, %.2f]", pub_dep["lo"], pub_dep["hi"]),
         sprintf("[%.2f, %.2f]", pub_excol["lo"], pub_excol["hi"]),
         sprintf("[%.2f, %.2f]", pub_rob["lo"], pub_rob["hi"]),
         sprintf("[%.2f, %.2f]", pub_parallel["lo"], pub_parallel["hi"]),
         sprintf("[%.2f, %.2f]", pub_crossover["lo"], pub_crossover["hi"]),
         sprintf("[%.2f, %.2f]", pub_g10["lo"], pub_g10["hi"]),
         sprintf("[%.2f, %.2f]", pub_clinician["lo"], pub_clinician["hi"]),
         sprintf("[%.2f, %.2f]", pub_selfreport["lo"], pub_selfreport["hi"]),
         sprintf("[%.2f, %.2f]", pub_outliers["lo"], pub_outliers["hi"]),
         sprintf("[%.2f, %.2f]", pub_response["lo"], pub_response["hi"]),
         sprintf("[%.2f, %.2f]", pub_remission["lo"], pub_remission["hi"]),
         sprintf("[%.2f, %.2f]", pub_multilevel["lo"], pub_multilevel["hi"]))
)
results_table_pub_summary
```

---

## RoBMA Analyses

```{r run-or-load}
if (run_fresh) {

  # ── Primary model ────────────────────────────────────────────────────────
  # Primary = data_main = Singleton et al.'s own published primary model
  # (12 studies) — verified to reproduce their reported g/CI/tau2/n exactly.
  set.seed(4821)
  robma_primary <- run_robma(prep_robma(data_main))

  # ── Subgroup models ──────────────────────────────────────────────────────
  subgroup_datasets <- list(
    dep       = data_dep,
    parallel  = data_parallel,
    crossover = data_crossover,
    excol     = data_excol,
    rob       = data_rob
  )

  robma_subgroups <- purrr::map(subgroup_datasets, \(df) run_robma(prep_robma(df)))

  # ── Sensitivity models ───────────────────────────────────────────────────
  sensitivity_datasets <- list(
    expanded   = data_expanded,
    g10        = data_g10,
    clinician  = data_clinician,
    selfreport = data_selfreport,
    outliers   = data_outliers
  )

  robma_sensitivity <- purrr::map(sensitivity_datasets, \(df) run_robma(prep_robma(df)))

  # ── Dichotomous outcomes ─────────────────────────────────────────────────
  # Run frequentist models first to extract log-RR and SE
  response_results <- runMetaAnalysis(data_response,
    which.run = "overall", es.measure = "RR", es.type = "raw",
    method.tau = "PM", method.tau.ci = "Q-Profile", hakn = TRUE,
    study.var = "study", arm.var.1 = "condition_arm1", arm.var.2 = "condition_arm2",
    measure.var = "instrument", w1.var = "n_arm1", w2.var = "n_arm2",
    time.var = "time_weeks", round.digits = 2)

  remission_results <- runMetaAnalysis(data_remission,
    which.run = "overall", es.measure = "RR", es.type = "raw",
    method.tau = "PM", method.tau.ci = "Q-Profile", hakn = TRUE,
    study.var = "study", arm.var.1 = "condition_arm1", arm.var.2 = "condition_arm2",
    measure.var = "instrument", w1.var = "n_arm1", w2.var = "n_arm2",
    time.var = "time_weeks", round.digits = 2)

  resp_df <- data.frame(
    study = response_results$model.overall$studlab,
    logRR = response_results$model.overall$TE,
    seRR  = response_results$model.overall$seTE)

  remiss_df <- data.frame(
    study = remission_results$model.overall$studlab,
    logRR = remission_results$model.overall$TE,
    seRR  = remission_results$model.overall$seTE)

  robma_response <- RoBMA(yi = resp_df$logRR,   sei = resp_df$seRR,
                          slab = resp_df$study,   measure = "RR",
                          seed = 4821, sample = 10000, burnin = 4000, silent = TRUE)

  robma_remission <- RoBMA(yi = remiss_df$logRR, sei = remiss_df$seRR,
                           slab = remiss_df$study, measure = "RR",
                           seed = 4821, sample = 10000, burnin = 4000, silent = TRUE)

  # ── Prior sensitivity ────────────────────────────────────────────────────
  robma_priors <- list(
    cauchy_05 = RoBMA(yi = prep_robma(data_main)$g_pos,
                      sei = prep_robma(data_main)$g_se,
                      slab = prep_robma(data_main)$study, measure = "SMD",
                      prior_effect = prior(distribution = "Cauchy",
                                           parameters   = list(location = 0, scale = 0.5),
                                           truncation   = list(0, Inf)),
                      seed = 4821, sample = 10000, burnin = 4000, silent = TRUE),

    cauchy_10 = RoBMA(yi = prep_robma(data_main)$g_pos,
                      sei = prep_robma(data_main)$g_se,
                      slab = prep_robma(data_main)$study, measure = "SMD",
                      prior_effect = prior(distribution = "Cauchy",
                                           parameters   = list(location = 0, scale = 1.0),
                                           truncation   = list(0, Inf)),
                      seed = 4821, sample = 10000, burnin = 4000, silent = TRUE),

    normal_01 = RoBMA(yi = prep_robma(data_main)$g_pos,
                      sei = prep_robma(data_main)$g_se,
                      slab = prep_robma(data_main)$study, measure = "SMD",
                      prior_effect = prior(distribution = "normal",
                                           parameters   = list(mean = 0, sd = 1),
                                           truncation   = list(0, Inf)),
                      seed = 4821, sample = 10000, burnin = 4000, silent = TRUE)
  )

  # ── Multilevel RoBMA (data_time: all timepoints, same 12 primary studies) ─
  # RoBMA 4.0.0 cluster argument — Bartoš, Maier & Wagenmakers (2026)
  ml_input_fresh <- data_time |>
    select(study, .g, .g_se) |>
    filter(!is.na(.g), !is.na(.g_se)) |>
    mutate(g_pos = -.g, g_se = .g_se)

  robma_multilevel <- RoBMA(
    yi       = ml_input_fresh$g_pos,
    sei      = ml_input_fresh$g_se,
    cluster  = ml_input_fresh$study,
    measure  = "SMD",
    seed     = 4821,
    sample   = 10000,
    burnin   = 4000,
    parallel = TRUE,
    silent   = TRUE
  )

  # Save all results together in a single call
  save(robma_primary, robma_subgroups, robma_sensitivity,
       robma_response, robma_remission, robma_priors, robma_multilevel,
       file = "psilodep-robma-results.RData")
  cat("All models (including multilevel) saved to psilodep-robma-results.RData\n")

} else {
  load("psilodep-robma-results.RData")
  cat("Pre-computed results loaded from psilodep-robma-results.RData\n")
}
```

---

## Primary RoBMA Results

```{r primary-summary}
summary(robma_primary)

# Extracted once here; referenced by inline `r` throughout this section and
# the next, so prose numbers can never drift from the fitted object.
.ps   <- summary(robma_primary)$inclusion_components
.pe   <- summary(robma_primary)$estimates
p_bf_effect <- round(.ps$inclusion_BF[1], 2)
p_bf_het    <- round(.ps$inclusion_BF[2], 2)
p_bf_pb     <- round(.ps$inclusion_BF[3], 2)
p_pp_pb     <- round(.ps$post_prob[3], 2)
p_mu_med    <- round(.pe[1, "0.5"], 2)
p_mu_lo     <- round(.pe[1, "0.025"], 2)
p_mu_hi     <- round(.pe[1, "0.975"], 2)

# Omega (weight function) CrI lower-bound range across p-value intervals —
# for the "Weight function interpretation" prose below.
.bias_est   <- summary(robma_primary)$estimates_bias
omega_lo_min <- round(min(.bias_est[2:6, "0.025"]), 2)
omega_lo_max <- round(max(.bias_est[2:6, "0.025"]), 2)
omega_med_min <- round(min(.bias_est[2:6, "0.5"]), 2)
omega_med_max <- round(max(.bias_est[2:6, "0.5"]), 2)
omega_all_at_ceiling <- all(.bias_est[2:6, "0.5"] == 1)
pet_med   <- round(.bias_est["PET",   "0.5"], 2)
peese_med <- round(.bias_est["PEESE", "0.5"], 2)
```

The primary RoBMA analysis yields three component Bayes Factors:

- **BF_effect**: evidence for a non-zero pooled effect
- **BF_het**: evidence for between-study heterogeneity
- **BF_pb**: evidence for publication bias

**BF interpretation scale (Jeffreys 1961; Kass & Raftery 1995):**

| BF range | Interpretation |
|---|---|
| 1 – 3 | Anecdotal / not worth more than a mention |
| 3 – 10 | **Moderate** evidence |
| 10 – 30 | Strong evidence |
| > 30 | Very strong / decisive |

BF_pb = `r p_bf_pb` falls in the **`r bf_label(p_bf_pb)`** range. It
updates the prior probability of publication bias from 0.50 to `r p_pp_pb`.
Overstatement of this finding is a primary risk to guard against.

The model-averaged, bias-corrected posterior for μ (`r p_mu_med` [`r p_mu_lo`,
`r p_mu_hi`]) should be compared directly to Singleton et al.'s own published
primary model, g = `r pub_primary["g"]` [`r pub_primary["lo"]`, `r pub_primary["hi"]`],
k = `r n_distinct(data_main$study)` — the same `r n_distinct(data_main$study)`-study
population used here. (Their "expanded inclusion criteria" sensitivity check,
using all `r n_distinct(data_expanded$study)` studies in the open database, is
reported alongside the other sensitivity analyses below: g = `r pub_expanded["g"]`
[`r pub_expanded["lo"]`, `r pub_expanded["hi"]`].)

**BF_het:** BF_het = `r p_bf_het`.

```{r primary-posterior-plot}
plot(robma_primary, parameter = "mu", prior = TRUE,
     main = "Posterior of μ (model-averaged) vs prior")
abline(v = pub_primary["g"], col = "firebrick", lty = 2, lwd = 1.5)
legend("topleft",
       legend = sprintf("Published g = %.2f (Singleton et al., 2026, primary model)", pub_primary["g"]),
       col = "firebrick", lty = 2, bty = "n", cex = 0.85)
```

```{r primary-weightfunction}
plot(robma_primary, parameter = "weightfunction",
     main = "Model-averaged publication bias weight function (ω)")
```

**Weight function interpretation:** `r if (omega_all_at_ceiling) "All ω posterior medians sit at 1.0 (maximum publication probability)" else sprintf("ω posterior medians range %.2f–%.2f (not uniformly at the ceiling)", omega_med_min, omega_med_max)`,
with credible intervals extending down to
`r omega_lo_min`–`r omega_lo_max` for the non-significant p-value ranges. This
does not mean "no bias" — it means the
data are consistent with either no bias or moderate bias, and the model averaging
(BF_pb = `r p_bf_pb`) is what shifts the posterior toward bias being present. The
diffuse ω posteriors indicate that the specific *form* of bias is uncertain; the
model averages over all specified weight function shapes.

**PET and PEESE posteriors:** PET median = `r pet_med`, PEESE median =
`r peese_med`, both with wide credible intervals. This indicates that neither
funnel-plot-based bias mechanism is individually supported — bias evidence in the
primary model comes from the weight function models, not from PET-PEESE. This is
an important nuance for the manuscript: BF_pb is not driven by a simple
small-study effect.

### Comparison with Egger's test

```{r egger-comparison}
# Egger's test on the primary model, computed live — nothing quoted from the
# paper. (data_main is Singleton et al.'s own published primary model, so
# this is directly their Egger's test, not a separate re-analysis of it.)
cat(sprintf("Primary model (k=%d) — Egger's test:\n", n_distinct(data_main$study)))
print(egger_primary)

egger_p <- egger_primary$p[1]
cat(sprintf("\nEgger's test (k=%d): p = %.4f\n", n_distinct(data_main$study), egger_p))
cat("RoBMA BF_pb =", p_bf_pb, "(posterior probability =", p_pp_pb, ")\n")
cat("\nNote: Egger's test has low power at this sample size.\n",
    "RoBMA's model-averaging approach is more sensitive to weak bias signals.\n")
```

---

## Prior Sensitivity Analysis

We test three alternative effect priors to verify that conclusions about
publication bias (BF_pb) and the bias-corrected effect (μ) are not
driven by the default Cauchy(0, 0.707) specification.

```{r prior-sensitivity-table}
extract_prior <- function(fit, label) {
  s    <- summary(fit)
  comp <- s$inclusion_components
  est  <- s$estimates
  tibble(
    Prior       = label,
    BF_effect   = round(comp$inclusion_BF[1], 2),
    PP_effect   = round(comp$post_prob[1],    2),
    BF_pb       = round(comp$inclusion_BF[3], 2),
    PP_pb       = round(comp$post_prob[3],    2),
    mu_median   = round(est[1, "0.5"],        2),
    mu_CrI      = sprintf("[%.2f, %.2f]", est[1, "0.025"], est[1, "0.975"]),
    ESS_mu      = round(est[1, "ESS"])
  )
}

prior_table <- bind_rows(
  extract_prior(robma_primary,          "Cauchy(0, 0.707) — default PSMA"),
  extract_prior(robma_priors$cauchy_05, "Cauchy(0, 0.5)   — conservative"),
  extract_prior(robma_priors$cauchy_10, "Cauchy(0, 1.0)   — diffuse"),
  extract_prior(robma_priors$normal_01, "Normal(0, 1)     — matches bayesmeta (Singleton et al.)")
)

prior_table
```

BF_pb ranges `r round(min(prior_table$BF_pb), 2)`–`r round(max(prior_table$BF_pb), 2)` and μ median ranges `r round(min(prior_table$mu_median), 2)`–`r round(max(prior_table$mu_median), 2)` across all four priors. Conclusions are robust to prior specification.

**Heterogeneity prior:** The default InvGamma(1, 0.15) prior for τ places most
mass below τ = 1, which is reasonable for standardised effect size differences.
An alternative InvGamma(1, 0.25) (more diffuse) was considered but not separately
run; given that BF_het = `r p_bf_het` (`r bf_label(p_bf_het)` evidence for
heterogeneity) and τ posteriors are dominated by the data at
k = `r n_distinct(data_expanded$study)`, heterogeneity prior sensitivity is
expected to be lower than effect prior sensitivity and is not a primary
concern here.

---

## Subgroup Analyses

Each subgroup mirrors a corresponding analysis in Singleton et al. (2026).
⚠ marks analyses with k < 8; BF_pb is highly prior-dependent at small k and
should be interpreted with caution.

```{r subgroup-results}
pub_vals <- list(
  dep       = pub_dep,
  parallel  = pub_parallel,
  crossover = pub_crossover,
  excol     = pub_excol,
  rob       = pub_rob
)

# Labels build their k-count from the actual filtered dataset, never typed —
# this is exactly the class of bug that broke the original submission.
label_k <- function(base, nm) {
  k <- n_distinct(datasets[[nm]]$study)
  sprintf("%s (k=%d)%s", base, k, if (k < 8) " ⚠" else "")
}
labels <- list(
  dep       = label_k("MDD/TRD diagnosis", "dep"),
  parallel  = label_k("Parallel design", "parallel"),
  crossover = label_k("Crossover only", "crossover"),
  excol     = label_k("Excl. open-label", "excol"),
  rob       = label_k("Excl. high RoB", "rob")
)

subgroup_table <- purrr::imap_dfr(robma_subgroups, \(fit, nm) {
  k   <- n_distinct(datasets[[nm]]$study)
  pv  <- pub_vals[[nm]]
  extract_robma(fit, labels[[nm]], k, pv["g"], pv["lo"], pv["hi"])
})

subgroup_table |>
  select(Analysis, k, `Pub. g`, BF_effect, BF_pb, mu_median, mu_CrI, Attenuation)
```

### Key subgroup finding: open-label studies drive the bias signal

```{r open-label-comparison}
bf_excol_val <- subgroup_table$BF_pb[grepl("open-label", subgroup_table$Analysis)]
bf_parallel_val <- subgroup_table$BF_pb[grepl("Parallel", subgroup_table$Analysis)]

cat("Publication bias Bayes Factors by design:\n\n")
cat(sprintf("  %s: BF_pb = %.2f (%s)\n",
    subgroup_table$Analysis[grepl("open-label", subgroup_table$Analysis)],
    bf_excol_val, bf_label(bf_excol_val)))
cat(sprintf("  %s: BF_pb = %.2f (%s)\n",
    subgroup_table$Analysis[grepl("Parallel", subgroup_table$Analysis)],
    bf_parallel_val, bf_label(bf_parallel_val)))
cat(sprintf("  Primary model (k=%d): BF_pb = %.2f (%s)\n",
    n_distinct(data_expanded$study), p_bf_pb, bf_label(p_bf_pb)))

# The "drops when open-label/parallel-only excluded" claim is only asserted if
# the numbers actually show it — computed, not stated on faith.
signal_drops <- bf_excol_val < p_bf_pb && bf_parallel_val < p_bf_pb
cat(sprintf("\nInterpretation: bias evidence is %s when open-label studies are\n",
    if (signal_drops) "lower" else "NOT lower"))
if (signal_drops) {
  cat("excluded (and in the parallel-only subset) than in the primary model —\n")
  cat("consistent with the bias signal being attributable to open-label designs\n")
  cat("(functional unblinding) rather than file-drawer suppression of blinded\n")
  cat("RCTs generally. Re-examine this framing if the pattern above does not\n")
  cat("hold on a future rerun.\n")
} else {
  cat("excluded than in the primary model. The 'open-label designs drive the\n")
  cat("signal' framing used elsewhere in this document does NOT hold for the\n")
  cat("current fit and must be revised before submission.\n")
}
```

---

## Sensitivity Analyses

```{r sensitivity-results}
pub_vals_sens <- list(
  expanded   = pub_expanded,
  g10        = pub_g10,
  clinician  = pub_clinician,
  selfreport = pub_selfreport,
  outliers   = pub_outliers
)

datasets_sens <- list(
  expanded   = data_expanded,
  g10        = data_g10,
  clinician  = data_clinician,
  selfreport = data_selfreport,
  outliers   = data_outliers
)

label_k_sens <- function(base, nm, marker = "") {
  k <- n_distinct(datasets_sens[[nm]]$study)
  sprintf("%s (k=%d)%s%s", base, k, marker, if (k < 8) " ⚠" else "")
}
labels_sens <- list(
  expanded   = label_k_sens("Expanded inclusion criteria", "expanded"),
  g10        = label_k_sens("Goodwin 10 mg arm", "g10"),
  clinician  = label_k_sens("Clinician-rated", "clinician"),
  selfreport = label_k_sens("Self-report", "selfreport", marker = " †"),
  outliers   = label_k_sens("Excl. Davis 2021", "outliers")
)

sensitivity_table <- purrr::imap_dfr(robma_sensitivity, \(fit, nm) {
  k   <- n_distinct(datasets_sens[[nm]]$study)
  pv  <- pub_vals_sens[[nm]]
  extract_robma(fit, labels_sens[[nm]], k, pv["g"], pv["lo"], pv["hi"])
})

sensitivity_table |>
  select(Analysis, k, `Pub. g`, BF_effect, BF_pb, mu_median, mu_CrI, Attenuation)
```

**† Self-report BF_pb = `r sensitivity_table$BF_pb[grepl("Self-report", sensitivity_table$Analysis)]`:**
k = `r n_distinct(data_selfreport$study)`, non-significant (g = `r pub_selfreport["g"]` [`r pub_selfreport["lo"]`,
`r pub_selfreport["hi"]`]), substantial heterogeneity. BF_pb this extreme at
this small a k is a signature of a numerically degenerate weight-function fit,
not strong evidence of bias in self-report outcomes specifically — do not
report at face value.

**Goodwin 10 mg (BF_pb = `r sensitivity_table$BF_pb[grepl("Goodwin", sensitivity_table$Analysis)]`):**
Using the 10 mg arm (genuinely lower dose-response) conflates lower efficacy
with publication bias. Interpret with caution; not straightforwardly comparable
to the primary model.

**Davis 2021 (Excl. Davis 2021: BF_pb = `r sensitivity_table$BF_pb[grepl("Davis", sensitivity_table$Analysis)]`):**
When the outlier (g = `r round(davis_g, 2)`) is excluded, publication bias
evidence drops to `r bf_label(sensitivity_table$BF_pb[grepl("Davis", sensitivity_table$Analysis)])`.
Davis 2021 appears to be a secondary driver of the bias signal.

---

## Dichotomous Outcomes

```{r dichotomous-results}
# Summarise
extract_dich <- function(fit, label, k, pub_RR, pub_lo, pub_hi) {
  s    <- summary(fit)
  comp <- s$inclusion_components
  est  <- s$estimates
  mu   <- est[1, "0.5"]
  tibble(
    Analysis    = label, k = k,
    `Pub. RR`   = round(pub_RR, 2),
    pub_lo_n    = round(pub_lo, 2),
    pub_hi_n    = round(pub_hi, 2),
    `Pub. CI`   = sprintf("[%.2f, %.2f]", pub_lo, pub_hi),
    BF_effect   = round(comp$inclusion_BF[1], 2),
    BF_pb       = round(comp$inclusion_BF[3], 2),
    `RoBMA RR`  = round(exp(mu), 2),
    mu_lo_n     = round(exp(est[1, "0.025"]), 2),
    mu_hi_n     = round(exp(est[1, "0.975"]), 2),
    `RoBMA CrI` = sprintf("[%.2f, %.2f]",
                          exp(est[1, "0.025"]), exp(est[1, "0.975"])),
    Attenuation = sprintf("%.0f%%", (1 - exp(mu) / pub_RR) * 100),
    ESS_mu      = round(est[1, "ESS"])
  )
}

.k_resp   <- n_distinct(data_response$study)
.k_remiss <- n_distinct(data_remission$study)
dich_table <- bind_rows(
  extract_dich(robma_response,  sprintf("Response (k=%d)%s", .k_resp, if (.k_resp < 8) " ⚠" else ""),
               .k_resp, pub_response["g"], pub_response["lo"], pub_response["hi"]),
  extract_dich(robma_remission, sprintf("Remission (k=%d)%s", .k_remiss, if (.k_remiss < 8) " ⚠" else ""),
               .k_remiss, pub_remission["g"], pub_remission["lo"], pub_remission["hi"])
)

dich_table

# BF_het / tau for both dichotomous fits, for the FE-vs-RE sentence below —
# checked live rather than asserted.
.resp_s   <- summary(robma_response)
.remiss_s <- summary(robma_remission)
resp_bf_het    <- round(.resp_s$inclusion_components$inclusion_BF[2], 2)
remiss_bf_het  <- round(.remiss_s$inclusion_components$inclusion_BF[2], 2)
resp_tau_med   <- round(.resp_s$estimates[2, "0.5"], 3)
remiss_tau_med <- round(.remiss_s$estimates[2, "0.5"], 3)
```

Attenuation and BF_pb for both dichotomous outcomes relative to Singleton et
al.'s published fixed-effects risk ratios (response: RR = `r pub_response["g"]`
[`r pub_response["lo"]`, `r pub_response["hi"]`], k=`r .k_resp`; remission: RR =
`r pub_remission["g"]` [`r pub_remission["lo"]`, `r pub_remission["hi"]`], k=`r .k_remiss`)
are reported in the table above — see `dich_table$Attenuation` and
`dich_table$BF_pb`. ⚠ k = `r .k_resp`–`r .k_remiss`; bias estimation has limited power.

**Fixed-effects dichotomous sensitivity:** Singleton et al. ran FE sensitivity
models for both response and remission. Checked live on this pinned data:
I² = `r resp_i2`% (response), `r remiss_i2`% (remission) — at these levels FE
and RE estimates are effectively identical. RoBMA captures this internally via
BF_het — response returns BF_het = `r resp_bf_het` (τ median = `r resp_tau_med`)
and remission BF_het = `r remiss_bf_het` (τ median = `r remiss_tau_med`),
confirming that fixed vs random effects makes no practical difference here. No
separate RoBMA run is needed.

---

## Comprehensive Results Table (Extended Data Table 1)

This table mirrors the TODO's "Extended Data Figure 2: Subgroup & Sensitivity
RoBMA" — all primary, subgroup, and sensitivity analyses in one place.
Flagged analyses (⚠) have k < 8; BF_pb is highly prior-dependent at small k.
Degenerate analyses (†) should not be reported at face value.

```{r full-results-table}
.k_primary <- n_distinct(data_main$study)

# Fixed-effect comparator row: reuses robma_primary's own posterior (same
# fit as the primary row) against Singleton et al.'s published fixed-effect
# sensitivity value, since RoBMA's BF_het already IS the fixed-vs-random
# comparison — no separate model needs fitting. Attenuation here compares
# the model-averaged posterior to the FE estimate specifically, not the
# random-effects primary estimate.
fixed_row <- extract_robma(robma_primary, sprintf("Fixed-effect model (k=%d) ‡", .k_primary),
                           .k_primary, pub_fixed["g"], pub_fixed["lo"], pub_fixed["hi"])

results_table <- bind_rows(
  extract_robma(robma_primary, sprintf("Primary (k=%d)", .k_primary), .k_primary,
                pub_primary["g"], pub_primary["lo"], pub_primary["hi"]),
  subgroup_table,
  sensitivity_table,
  fixed_row
)

results_table |>
  select(Analysis, k, `Pub. g`, `Pub. CI`, BF_effect, PP_effect,
         BF_pb, PP_pb, mu_median, mu_CrI, Attenuation, ESS_mu, Rhat_mu) |>
  print(n = Inf, width = Inf)
```

```{r save-ed-table}
# Save the comprehensive table as a formatted CSV for the submission package
results_table |>
  select(Analysis, k, `Pub. g`, `Pub. CI`, BF_effect, PP_effect,
         BF_pb, PP_pb, mu_median, mu_CrI, Attenuation, ESS_mu, Rhat_mu) |>
  write.csv("ED_Table1_comprehensive_results.csv", row.names = FALSE)
cat("Extended Data Table 1 saved to ED_Table1_comprehensive_results.csv\n")
```

---

## MCMC Diagnostics

All models must satisfy R-hat ≤ 1.01 and ESS_μ > 400 for results to be
trustworthy. ⚠ flags borderline values.

```{r mcmc-diagnostics}
diag_table <- purrr::imap_dfr(
  c(list(primary = robma_primary),
    robma_subgroups,
    robma_sensitivity,
    list(response = robma_response, remission = robma_remission,
         multilevel = robma_multilevel)),
  \(fit, nm) {
    est <- summary(fit)$estimates
    tibble(
      Model    = nm,
      ESS_mu   = round(est[1, "ESS"]),
      ESS_tau  = round(est[2, "ESS"]),
      Rhat_mu  = round(est[1, "R_hat"], 3),
      Rhat_tau = round(est[2, "R_hat"], 3),
      Flag     = if_else(est[1, "R_hat"] > 1.01 | est[1, "ESS"] < 400, "⚠", "✓")
    )
  }
)

diag_table
```

---

## Figures

### Figure 1 (main): Three-panel comparison

```{r figure-1, fig.width=10, fig.height=10}
# ── Panel A: posterior of μ vs prior ─────────────────────────────────────────
# TODO called for BF_effect and BF_pb to be annotated directly on panel A.
# In the final figure these are reported in the figure caption and in panel C's
# BF_pb column rather than as text overlays on panel A, to avoid crowding the
# density plot. The caption text below is generated dynamically from
# pub_primary / p_bf_effect / p_bf_pb — never hardcoded.
#
# Captured via pdf() — RoBMA's plot() opens an internal graphics device that
# desynchronises the png() capture stack. pdf() is file-based and immune.
tmp_pdf_A <- tempfile(fileext = ".pdf")
pdf(tmp_pdf_A, width = 5.5, height = 4.5)
par(mar = c(5, 5, 3, 6))  # mar[4] = 6 to clear the right y-axis labels
plot(robma_primary, parameter = "mu", prior = TRUE,
     main = expression(bold("a") ~~ "Posterior of" ~ mu ~ "vs prior"))
abline(v = pub_primary["g"], col = "firebrick", lty = 2, lwd = 1.8)
usr <- par("usr")
text(x = pub_primary["g"] + 0.05, y = usr[4] * 0.70,
     sprintf("Published\ng = %.2f", pub_primary["g"]), col = "firebrick", adj = 0, cex = 0.82)
invisible(dev.off())
magick::image_write(magick::image_read_pdf(tmp_pdf_A, density = 300),
                    "tmp_pA.png", format = "png")

# ── Panel B: ω posteriors (ggplot2 — immune to device conflicts) ─────────────
bias_est <- summary(robma_primary)$estimates_bias
omega_df <- data.frame(
  interval = c("(0.025,\n0.05]", "(0.05,\n0.5]", "(0.5,\n0.95]",
                "(0.95,\n0.975]", "(0.975,\n1]"),
  median   = bias_est[2:6, "0.5"],
  lo       = bias_est[2:6, "0.025"],
  hi       = bias_est[2:6, "0.975"]
) |> mutate(interval = factor(interval, levels = interval))

pB_plot <- ggplot(omega_df, aes(x = interval, y = median)) +
  geom_hline(yintercept = 1, linetype = "dashed", colour = "grey60") +
  geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.18,
                colour = "grey40", linewidth = 0.7) +
  geom_point(size = 3.5, colour = "#1f4e79") +
  scale_y_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.25),
                     name = expression(omega ~ "posterior median [95% CrI]")) +
  labs(x = "One-sided p-value interval",
       title = expression(bold("b") ~~ "Weight function (" * omega * ")"),
       subtitle = "Dashed = \u03c9 = 1 (no selection)") +
  theme_classic(base_size = 11) +
  theme(plot.title    = element_text(size = 10, face = "bold"),
        plot.subtitle = element_text(size = 8.5, colour = "grey45"),
        axis.text.x   = element_text(size = 8))
ggsave("tmp_pB.png", pB_plot, width = 5, height = 4.5, dpi = 300)

# ── Panel C: comparison forest ───────────────────────────────────────────────
# Single-level rows (warning flags derived from k)
base_rows <- results_table |>
  filter(!grepl("Self-report|Goodwin 10 mg|Crossover|Fixed-effect", Analysis)) |>
  mutate(
    Analysis = str_remove(Analysis, " \u26a0$"),
    Analysis = if_else(k < 8, paste0(Analysis, " \u26a0"), Analysis),
    pub_lo   = pub_lo_n,
    pub_hi   = pub_hi_n,
  ) |>
  select(Analysis, k, `Pub. g`, pub_lo, pub_hi, BF_pb, mu_median, mu_lo_n, mu_hi_n)

# Multilevel row — published comparison is the CHE model (Singleton et al.)
# Computed locally (not from the Multilevel section below, which runs later
# in document order) so this chunk doesn't depend on section ordering.
.s_ml_local <- summary(robma_multilevel)
ml_label <- sprintf("Multilevel RoBMA (k=%d) †", nrow(data_time))
ml_row <- tibble(
  Analysis  = ml_label,
  k         = nrow(data_time),
  `Pub. g`  = unname(pub_multilevel["g"]),
  pub_lo    = unname(pub_multilevel["lo"]), pub_hi = unname(pub_multilevel["hi"]),
  BF_pb     = round(.s_ml_local$inclusion_components$inclusion_BF[3], 2),
  mu_median = round(.s_ml_local$estimates["mu", "0.5"], 2),
  mu_lo_n   = round(.s_ml_local$estimates["mu", "0.025"], 2),
  mu_hi_n   = round(.s_ml_local$estimates["mu", "0.975"], 2)
)

# Combine: multilevel at bottom (row = 1), single-level rows 2–9
all_labels <- c(rev(base_rows$Analysis), ml_label)
forest_df  <- bind_rows(base_rows, ml_row) |>
  mutate(Analysis = factor(Analysis, levels = rev(all_labels)),
         row      = as.integer(Analysis))

# x-axis range derived from the actual plotted CIs, not hardcoded — a fixed
# range previously clipped the multilevel row's CI (mu_lo_n = -0.33 fell just
# outside a hardcoded lower limit of -0.3), which ggplot2 silently drops as
# NA rather than warning loudly: the errorbar's left cap and connecting line
# vanished, leaving only the orphaned right cap visible. Deriving the range
# from the data makes this class of bug structurally impossible.
x_data_lo   <- min(c(forest_df$pub_lo, forest_df$mu_lo_n), na.rm = TRUE)
x_data_hi   <- max(c(forest_df$pub_hi, forest_df$mu_hi_n), na.rm = TRUE)
x_axis_lo   <- x_data_lo - 0.05
x_bf_label  <- x_data_hi + 0.15
x_axis_hi   <- x_bf_label + 0.6   # room for the "BF[pb]==X.XX" annotation text

pC_plot <- ggplot(forest_df) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  # Dotted separator between multilevel and single-level rows — derived from
  # nrow(ml_row) (always 1 row) so this doesn't silently misalign if the row
  # composition of results_table ever changes.
  geom_hline(yintercept = nrow(ml_row) + 0.55, linetype = "dotted",
             colour = "grey60", linewidth = 0.4) +
  geom_errorbar(aes(xmin = pub_lo, xmax = pub_hi, y = row + 0.2),
                width = 0.15, colour = "#1f4e79", linewidth = 0.6,
                orientation = "y") +
  geom_point(aes(x = `Pub. g`, y = row + 0.2), shape = 16, size = 2.8,
             colour = "#1f4e79") +
  geom_errorbar(aes(xmin = mu_lo_n, xmax = mu_hi_n, y = row - 0.2),
                width = 0.15, colour = "#c55a11", linewidth = 0.6,
                orientation = "y") +
  geom_point(aes(x = mu_median, y = row - 0.2), shape = 15, size = 2.8,
             colour = "#c55a11") +
  geom_text(aes(x = x_bf_label, y = row,
                label = sprintf("BF[pb]==%.2f", BF_pb)),
            parse = TRUE, size = 2.8, hjust = 0, colour = "grey30") +
  scale_y_continuous(breaks = forest_df$row, labels = forest_df$Analysis,
                     limits = c(0.5, nrow(forest_df) + 0.6)) +
  scale_x_continuous(limits = c(x_axis_lo, x_axis_hi), breaks = scales::breaks_pretty(n = 5),
                     name = "Effect size (Hedges' g)") +
  labs(y = NULL,
       subtitle = "Navy \u25cf = published [95% CI];  Orange \u25a0 = RoBMA bias-corrected [95% CrI]") +
  theme_classic(base_size = 11) +
  theme(axis.text.y   = element_text(size = 8.5),
        plot.subtitle = element_text(size = 9, colour = "grey40"))
ggsave("tmp_pC.png", pC_plot, width = 10, height = 7, dpi = 300)

# ── Compose with magick ───────────────────────────────────────────────────────
img_A  <- magick::image_read("tmp_pA.png")
img_B  <- magick::image_read("tmp_pB.png")
h_max  <- max(magick::image_info(img_A)$height, magick::image_info(img_B)$height)
top    <- magick::image_append(
  c(magick::image_resize(img_A, paste0("x", h_max)),
    magick::image_resize(img_B, paste0("x", h_max))))
bottom <- magick::image_read("tmp_pC.png")
w      <- magick::image_info(bottom)$width
cap    <- magick::image_blank(w, 160, color = "white") |>
  magick::image_annotate(
    # Plain ASCII only — Unicode subscripts and special symbols do not render
    # reliably in magick's system font pipeline.
    # Two-line caption with \n to prevent right-edge clipping.
    paste0(
      sprintf("a: posterior of mu (black) vs prior (grey); dashed = published g = %.2f (Singleton et al. 2026, primary model); ", pub_primary["g"]),
      sprintf("primary model: BF_effect = %.2f, BF_pb = %.2f.\n", p_bf_effect, p_bf_pb),
      "b: omega posterior median [95% CrI] per p-value interval; dashed = omega = 1 (no selection).\n",
      "c: BF_pb per row. Triangle = k < 8; interpret BF_pb cautiously. ",
      sprintf("Dagger (dagger) = multilevel RoBMA (k = %d effect sizes, %d study clusters); ",
              nrow(data_time), n_distinct(data_time$study)),
      "published = CHE model estimate (Singleton et al.); within-study selection caveat applies."
    ),
    size = 24, color = "grey45", gravity = "NorthWest", location = "+20+12")
fig1_composed <- magick::image_append(
  c(magick::image_scale(top, paste0(w, "x")), bottom, cap), stack = TRUE)
magick::image_write(fig1_composed, "fig1_robma_main.jpg",
                    format = "jpeg", quality = 95)
file.remove(c("tmp_pA.png", "tmp_pB.png", "tmp_pC.png"))
cat("Figure 1 saved:", magick::image_info(fig1_composed)$width, "x",
    magick::image_info(fig1_composed)$height, "px\n")
```

### Extended Data Figure 1: Prior sensitivity

```{r ed-fig1, fig.width=9, fig.height=4.5}
prior_plot_df <- prior_table |>
  mutate(Prior = factor(Prior, levels = rev(Prior)),
         row   = as.integer(Prior))

prior_plot_df <- prior_plot_df |>
  mutate(mu_lo_n = as.numeric(str_extract(mu_CrI, "-?[0-9.]+")),
         mu_hi_n = as.numeric(str_extract(mu_CrI, "(?<=, )-?[0-9.]+")))

# x-axis range derived from data, not hardcoded — see the identical fix (and
# its rationale) in Figure 1 Panel C above.
ed1_x_lo    <- min(prior_plot_df$mu_lo_n, na.rm = TRUE) - 0.05
ed1_x_hi_dat<- max(prior_plot_df$mu_hi_n, na.rm = TRUE)
ed1_x_label <- ed1_x_hi_dat + 0.15
ed1_x_hi    <- ed1_x_label + 0.85   # room for the "BF[effect]==X BF[pb]==X" annotation

ed1 <- ggplot(prior_plot_df) +
  geom_point(aes(x = mu_median, y = row), shape = 18, size = 4,
             colour = "#c55a11") +
  geom_errorbar(aes(xmin = mu_lo_n, xmax = mu_hi_n, y = row),
    width = 0.2, colour = "#c55a11", linewidth = 0.7,
    orientation = "y") +
  geom_text(aes(x = ed1_x_label, y = row,
                label = sprintf("BF[effect]==%.2f~~BF[pb]==%.2f",
                                BF_effect, BF_pb)),
            parse = TRUE, size = 3.2, hjust = 0) +
  geom_vline(xintercept = 0,       linetype = "dashed", colour = "grey60") +
  geom_vline(xintercept = p_mu_med, linetype = "dotted", colour = "#c55a11", alpha = 0.5) +
  scale_y_continuous(breaks = prior_plot_df$row, labels = prior_plot_df$Prior) +
  scale_x_continuous(limits = c(ed1_x_lo, ed1_x_hi), breaks = scales::breaks_pretty(n = 5)) +
  labs(x = "RoBMA μ median [95% CrI]", y = NULL,
       title = "Extended Data Fig. 1 — Prior sensitivity analysis",
       subtitle = sprintf("Dotted vertical = default PSMA estimate (μ = %.2f)", p_mu_med)) +
  theme_classic(base_size = 11) +
  theme(plot.title    = element_text(face = "bold", size = 11),
        plot.subtitle = element_text(size = 8.5, colour = "grey40"),
        axis.text.y   = element_text(size = 9))

ed1
ggsave("fig_ED1_prior_sensitivity.jpg", ed1, width = 9, height = 4.5, dpi = 300)
```

### Extended Data Figure 2: Dichotomous outcomes

```{r ed-fig2, fig.width=9, fig.height=3.8}
dich_plot_df2 <- dich_table |>
  mutate(Analysis = factor(Analysis, levels = rev(Analysis)),
         row    = as.integer(Analysis),
         pub_lo = pub_lo_n, pub_hi = pub_hi_n,
         mu_lo  = mu_lo_n,  mu_hi  = mu_hi_n)

# x-axis range derived from data, not hardcoded — see the identical fix (and
# its rationale) in Figure 1 Panel C above.
ed2_x_lo    <- min(c(dich_plot_df2$pub_lo, dich_plot_df2$mu_lo), na.rm = TRUE) - 0.2
ed2_x_hi_dat<- max(c(dich_plot_df2$pub_hi, dich_plot_df2$mu_hi), na.rm = TRUE)
ed2_x_label <- ed2_x_hi_dat + 0.4
ed2_x_hi    <- ed2_x_label + 2   # room for the "BF[pb]==X.XX" annotation

ed2 <- ggplot(dich_plot_df2) +
  geom_vline(xintercept = 1, linetype = "dashed", colour = "grey60") +
  geom_errorbar(aes(xmin = pub_lo, xmax = pub_hi, y = row + 0.2),
                width = 0.12, colour = "#1f4e79", linewidth = 0.7,
                orientation = "y") +
  geom_point(aes(x = `Pub. RR`, y = row + 0.2), shape = 16, size = 3,
             colour = "#1f4e79") +
  geom_errorbar(aes(xmin = mu_lo, xmax = mu_hi, y = row - 0.2),
                width = 0.12, colour = "#c55a11", linewidth = 0.7,
                orientation = "y") +
  geom_point(aes(x = `RoBMA RR`, y = row - 0.2), shape = 15, size = 3,
             colour = "#c55a11") +
  # BF_pb annotation — mirrors style of panel c in Fig. 1
  geom_text(aes(x = ed2_x_label, y = row,
                label = sprintf("BF[pb]==%.2f", BF_pb)),
            parse = TRUE, size = 3.2, hjust = 0, colour = "grey30") +
  scale_y_continuous(breaks = dich_plot_df2$row,
                     labels = dich_plot_df2$Analysis) +
  scale_x_continuous(limits = c(ed2_x_lo, ed2_x_hi), breaks = scales::breaks_pretty(n = 6),
                     name = "Risk Ratio") +
  labs(
    y        = NULL,
    title    = "Extended Data Fig. 2 \u2014 Dichotomous outcomes",
    subtitle = "Navy \u25cf = published [95% CI];  Orange \u25a0 = RoBMA bias-corrected [95% CrI]",
    # Avoid \u26a0 — may not have JPEG font glyphs; ggplot2 renders it as △
    caption  = "Triangle = k < 8; BF_pb has limited power and should be interpreted cautiously."
  ) +
  theme_classic(base_size = 11) +
  theme(
    plot.title    = element_text(face = "bold", size = 11),
    plot.subtitle = element_text(size = 8.5, colour = "grey40"),
    plot.caption  = element_text(size = 8,   colour = "grey45", hjust = 0)
  )

ed2
ggsave("fig_ED2_dichotomous.jpg", ed2, width = 9, height = 3.8, dpi = 300)
```

### Extended Data Figure 3: MCMC diagnostics

```{r ed-fig3}
diag_table |> print(n = Inf)
```

---

## Scope Limitations

The following analyses from Singleton et al. (2026) are **outside RoBMA's scope**
and are not replicated here. Each is addressed in the manuscript's Methods or Discussion.

| Analysis in Singleton et al. | RoBMA status | Reason |
|---|---|---|
| Three-level CHE model (k = `r nrow(data_time)`) | **Replicated and extended** — see Multilevel RoBMA section below | RoBMA 4.0 `cluster` argument implements compound-symmetric structure (Bartoš, Maier & Wagenmakers, 2026); adds publication bias correction |
| Rho sensitivity sweep | Not replicated | Specific to CHE; not applicable to RoBMA |
| Meta-regression on time_days | Not replicated | Out of scope; β = `r che_timereg_beta`/day (p = `r che_timereg_p`) live-recomputed above |
| Design moderation test | Partial | Parallel/crossover RoBMA runs serve as substitute |
| Fixed-effects model | Captured internally | RoBMA models fixed effects via BF_het component |
| bayesmeta sensitivity | Superseded | RoBMA extends bayesmeta by adding publication bias correction |

---

## Multilevel RoBMA (Extending the CHE Model)

RoBMA 4.0.0 supports multilevel (clustered) meta-analysis via the `cluster`
argument, implementing the same compound-symmetric structure as the three-level
CHE model in Singleton et al. (Bartoš, Maier & Wagenmakers, 2026, *Behavior
Research Methods*), fit on the same `r n_distinct(data_time$study)`-study
population as their own CHE model (all timepoints retained, k = `r nrow(data_time)`
effect sizes), partitioning heterogeneity into
within-study (τ_within, across timepoints) and between-study (τ_between)
components simultaneously with bias adjustment.

**Important methodological caveat:** Standard publication bias selection models
assume that each effect size could, in principle, be an unpublished study.
Within-study effect sizes from different timepoints are all from the same
*published* paper — there is no traditional within-study publication selection.
The weight functions in the multilevel model therefore target study-level bias,
but the PEESE component may conflate within-study timepoint heterogeneity with
funnel plot asymmetry. Interpret with this in mind; the single-level primary
RoBMA (using one effect size per study) remains the most methodologically
straightforward analysis for publication bias detection.

```{r multilevel-data}
# Multi-timepoint data: same studies as Singleton et al.'s own CHE model
# (data_main population), all timepoints retained.
ml_input <- data_time |>
  select(study, .g, .g_se) |>
  filter(!is.na(.g), !is.na(.g_se)) |>
  mutate(g_pos = -.g, g_se = .g_se)  # negate: positive = psilocybin beneficial

ml_input |>
  group_by(study) |>
  summarise(n_timepoints = n(), .groups = "drop") |>
  arrange(desc(n_timepoints))
```

```{r multilevel-robma-note}
# robma_multilevel is fitted in the main run-or-load chunk (run_fresh = TRUE)
# or loaded from psilodep-robma-results.RData (run_fresh = FALSE).
# Both paths produce the same object; no separate fitting call is needed here.
cat("robma_multilevel loaded:", inherits(robma_multilevel, "RoBMA"), "\n")
cat("k =", nrow(ml_input), "| clusters =", n_distinct(ml_input$study), "\n")
```

```{r multilevel-results}
summary(robma_multilevel)
```

```{r multilevel-heterogeneity}
# Heterogeneity decomposition: within- vs between-study
summary_heterogeneity(robma_multilevel)
```

**Results interpretation:**

```{r multilevel-comparison}
s_ml <- summary(robma_multilevel)

# Extracted once here; referenced by inline `r` in "Key findings" below and
# by Panel C's ml_row in the Figures section (this chunk runs first).
ml_mu_med   <- round(s_ml$estimates["mu", "0.5"], 2)
ml_mu_lo    <- round(s_ml$estimates["mu", "0.025"], 2)
ml_mu_hi    <- round(s_ml$estimates["mu", "0.975"], 2)
ml_bf_effect<- round(s_ml$inclusion_components$inclusion_BF[1], 2)
ml_bf_het   <- round(s_ml$inclusion_components$inclusion_BF[2], 2)
ml_bf_pb    <- round(s_ml$inclusion_components$inclusion_BF[3], 2)

che_tau2 <- sum(.che_fit$sigma2)
che_n    <- sum(data_main$n_arm1 + data_main$n_arm2, na.rm = TRUE)
che_k    <- n_distinct(data_main$study)

cat("Multilevel RoBMA vs CHE model (Singleton et al. methodology, live-fit here)\n\n")

cat(sprintf("CHE (frequentist, no bias correction, k=%d, n=%d): mu = %.2f [%.2f, %.2f], tau2 = %.2f\n\n",
    che_k, che_n, pub_multilevel["g"], pub_multilevel["lo"], pub_multilevel["hi"], che_tau2))

cat(sprintf("Multilevel RoBMA (bias-corrected, same %d studies, k=%d effect sizes):\n",
    n_distinct(data_time$study), nrow(data_time)))
cat(sprintf("  μ median = %.2f [%.2f, %.2f]\n",
            s_ml$estimates["mu","0.5"],
            s_ml$estimates["mu","0.025"],
            s_ml$estimates["mu","0.975"]))
cat(sprintf("  BF_effect = %.2f  (posterior prob = %.2f)\n",
            s_ml$inclusion_components$inclusion_BF[1],
            s_ml$inclusion_components$post_prob[1]))
cat(sprintf("  BF_het    = %.2f  (posterior prob = %.2f)\n",
            s_ml$inclusion_components$inclusion_BF[2],
            s_ml$inclusion_components$post_prob[2]))
cat(sprintf("  BF_pb     = %.2f  (posterior prob = %.2f)\n",
            s_ml$inclusion_components$inclusion_BF[3],
            s_ml$inclusion_components$post_prob[3]))
cat(sprintf("  ESS_mu    = %d  R-hat = %.3f\n",
            round(s_ml$estimates["mu","ESS"]),
            s_ml$estimates["mu","R_hat"]))
cat(sprintf("\n%s ESS_mu = %d (target: 400). Estimates for mu are\n",
    if (s_ml$estimates["mu","ESS"] < 400) "⚠" else "✓",
    round(s_ml$estimates["mu","ESS"])))
cat("  less stable than the primary model; interpret with caution.\n")
.ml_tau_ess   <- round(s_ml$estimates["tau", "ESS"])
.ml_bias_ess  <- summary(robma_multilevel)$estimates_bias[, "ESS"]
.ml_omega_ess_range <- range(.ml_bias_ess[2:6], na.rm = TRUE)
cat(sprintf("  Heterogeneity (tau) is well-sampled: ESS = %d. Weight-function\n", .ml_tau_ess))
cat(sprintf("  (omega) components: ESS %d-%d. PET/PEESE ESS is lower (%d/%d) —\n",
    round(.ml_omega_ess_range[1]), round(.ml_omega_ess_range[2]),
    round(.ml_bias_ess["PET"]), round(.ml_bias_ess["PEESE"])))
cat("  interpret those two components with the same caution as mu.\n\n")

cat("Heterogeneity decomposition:\n")
het    <- summary_heterogeneity(robma_multilevel)
het_df <- het$estimates   # data.frame: rows = parameters, cols = Mean/Median/0.025/0.975
cat(sprintf("  τ_total   = %.3f [%.3f, %.3f]\n",
            het_df["tau",        "Median"], het_df["tau",        "0.025"], het_df["tau",        "0.975"]))
cat(sprintf("  τ_between = %.3f [%.3f, %.3f]  (between studies)\n",
            het_df["tau [between]","Median"], het_df["tau [between]","0.025"], het_df["tau [between]","0.975"]))
cat(sprintf("  τ_within  = %.3f [%.3f, %.3f]  (within studies, across timepoints)\n",
            het_df["tau [within]", "Median"], het_df["tau [within]", "0.025"], het_df["tau [within]", "0.975"]))
cat(sprintf("  ρ (between allocation) = %.3f [%.3f, %.3f]\n",
            het_df["rho",        "Median"], het_df["rho",        "0.025"], het_df["rho",        "0.975"]))
```

**Key findings from multilevel RoBMA:** (all values below are pulled live from
`s_ml` / `p_bf_pb` etc. — nothing here is asserted independently of the fit.)

1. **BF_pb = `r ml_bf_pb`** (`r bf_label(ml_bf_pb)`) vs the single-level primary
   model (BF_pb = `r p_bf_pb`, `r bf_label(p_bf_pb)`).

2. **μ median = `r ml_mu_med` [`r ml_mu_lo`, `r ml_mu_hi`]** vs g = `r pub_multilevel["g"]`
   in the CHE model.

3. **BF_effect = `r ml_bf_effect`** (`r bf_label(ml_bf_effect)`) vs the
   single-level primary model (BF_effect = `r p_bf_effect`, `r bf_label(p_bf_effect)`).

4. **ρ (between-study allocation)** — see the heterogeneity decomposition table above.

5. **PEESE component** — see `summary(robma_multilevel)` output above for the
   PET/PEESE posteriors; interpret with the within-study caveat noted above.

---

**What RoBMA cannot correct regardless of results:**

- **Functional unblinding:** psilocybin produces unmistakable subjective effects;
  participants in every trial knew their allocation. Expectancy effects are not
  modeled by weight functions. This is the most important limitation — it is
  independent of publication bias and cannot be statistically corrected.
- **Selective outcome reporting *within* studies:** RoBMA's weight function
  mechanism models suppression of whole studies, not suppression of unfavorable
  outcomes within published studies.
- **Selective timepoint reporting:** The CHE model in Singleton et al. addressed
  within-study correlation across multiple follow-up timepoints. RoBMA uses only
  one effect size per study (primary timepoint), meaning that if investigators
  selectively reported favorable timepoints *within* studies, this form of bias
  is not captured.
- **Primary instrument/timepoint selection as researcher degrees of freedom:**
  The rules used to select the primary instrument and timepoint per study are
  themselves analytical decisions. RoBMA treats the selected effect sizes as
  given and does not model uncertainty arising from this upstream selection step.
- **Setting dependency:** All trials used structured therapeutic protocols
  (preparation, monitored dosing, integration). Effect sizes reflect
  psilocybin + therapy, not the molecule alone.
- **Heterogeneous populations:** Studies include MDD, TRD, cancer-related
  depression, and palliative care populations. RoBMA pools across these without
  moderation, which the subgroup analyses partially address.
- **Heterogeneous comparators:** Control conditions include placebo, niacin,
  microcrystalline cellulose, and active placebos. Variation in comparator
  inertness affects absolute effect size estimates; RoBMA does not model this.

**Exclusion decisions inherited from Singleton et al.:**

- *Carhart-Harris 2021* excluded: used an active comparator (escitalopram) rather
  than placebo, making the effect size metric non-comparable to placebo-controlled
  trials. This exclusion is well-justified and does not bias our RoBMA.
- *Grob 2011* excluded: a pilot study in cancer patients with life-threatening
  illness — a distinct population with different prognosis and expectancy dynamics.
- *Krempien 2023 (12 mg arm)* excluded from primary; high-dose arm included in
  expanded analysis. If the excluded low-dose arm showed null results and was
  suppressed, this would bias the expanded but not the primary analysis.

---

## Summary and Conclusions

```{r summary}
cat("═══════════════════════════════════════════════════════════════\n")
cat("PRIMARY RESULT\n")
cat("───────────────────────────────────────────────────────────────\n")
s_prim <- summary(robma_primary)
cat(sprintf("  BF_effect = %.2f  (PP = %.2f)\n",
            s_prim$inclusion_components$inclusion_BF[1],
            s_prim$inclusion_components$post_prob[1]))
cat(sprintf("  BF_het    = %.2f  (PP = %.2f)\n",
            s_prim$inclusion_components$inclusion_BF[2],
            s_prim$inclusion_components$post_prob[2]))
cat(sprintf("  BF_pb     = %.2f  (PP = %.2f)\n",
            s_prim$inclusion_components$inclusion_BF[3],
            s_prim$inclusion_components$post_prob[3]))
cat(sprintf("  μ median  = %.2f  [%.2f, %.2f]\n",
            s_prim$estimates[1,"0.5"],
            s_prim$estimates[1,"0.025"],
            s_prim$estimates[1,"0.975"]))
cat(sprintf("  Published:  g = %.2f  [%.2f, %.2f]  (Singleton et al., primary model, k=%d)\n",
            pub_primary["g"], pub_primary["lo"], pub_primary["hi"], n_distinct(data_main$study)))
cat(sprintf("  Attenuation: ~%.0f%%\n",
            (1 - s_prim$estimates[1,"0.5"] / pub_primary["g"]) * 100))
cat("\n")
cat("KEY SUBGROUP FINDING\n")
cat("───────────────────────────────────────────────────────────────\n")
bf_davis_val <- sensitivity_table$BF_pb[grepl("Davis", sensitivity_table$Analysis)]
cat(sprintf("  %s: BF_pb = %.2f\n",
    subgroup_table$Analysis[grepl("open-label", subgroup_table$Analysis)],
    bf_excol_val))
cat(sprintf("  %s: BF_pb = %.2f\n",
    sensitivity_table$Analysis[grepl("Davis", sensitivity_table$Analysis)],
    bf_davis_val))
signal_drops_summary <- bf_excol_val < p_bf_pb && bf_davis_val < p_bf_pb
cat(sprintf("  -> Bias evidence is %s in both subsets than in the primary model (BF_pb = %.2f):\n",
    if (signal_drops_summary) "lower" else "NOT uniformly lower", p_bf_pb))
cat(sprintf("     %s attributable mainly to open-label/outlier studies.\n\n",
    if (signal_drops_summary) "consistent with the bias signal being" else "the 'open-label/outlier driven' framing is NOT supported —"))
cat("PRIOR SENSITIVITY\n")
cat("───────────────────────────────────────────────────────────────\n")
cat(sprintf("  BF_pb range: %.2f – %.2f across four priors\n",
            min(prior_table$BF_pb), max(prior_table$BF_pb)))
cat(sprintf("  μ median range: %.2f – %.2f across four priors\n",
            min(prior_table$mu_median), max(prior_table$mu_median)))
cat("\n")
cat("DICHOTOMOUS OUTCOMES\n")
cat("───────────────────────────────────────────────────────────────\n")
cat(sprintf("  Response:  RR = %.2f %s  (published: %.2f)  %s\n",
            dich_table$`RoBMA RR`[1], dich_table$`RoBMA CrI`[1],
            dich_table$`Pub. RR`[1], dich_table$Attenuation[1]))
cat(sprintf("  Remission: RR = %.2f %s  (published: %.2f)  %s\n",
            dich_table$`RoBMA RR`[2], dich_table$`RoBMA CrI`[2],
            dich_table$`Pub. RR`[2], dich_table$Attenuation[2]))
cat("═══════════════════════════════════════════════════════════════\n")
```

These results do not overturn Singleton et al. (2026). They refine the
uncertainty around the effect estimate and provide formal evidence about
publication bias in this literature (BF_pb = `r p_bf_pb`), with a
bias-corrected pooled effect approximately `r sprintf("%.0f", (1 - p_mu_med/pub_primary["g"])*100)`%
smaller than the frequentist estimate (posterior probability = `r p_pp_pb`).
`r if (signal_drops_summary) "The bias signal is attributable mainly to open-label and outlier studies rather than suppression of blinded RCTs generally (see the open-label/Davis 2021 comparison above)." else "The open-label/outlier subgroup comparison above does NOT currently support the 'driven by open-label designs' framing — revise this conclusion before submission."`

We recommend RoBMA be incorporated as a standard sensitivity analysis in future
updates of this living systematic review.

---

## Session Info

```{r session-info}
sessionInfo()
```
