---
layout: single
title: "Reproducibility Guide: RoBMA Re-analysis of Singleton et al. (2026)"
output:
  md_document:
    variant: markdown_github
    preserve_yaml: true
---

This document provides a complete reproducibility guide for the Robust Bayesian
Meta-Analysis (RoBMA) re-analysis of Singleton et al. (2026), submitted as a
Matters Arising to *Nature Mental Health*.

**Target paper:** Singleton SP, Sevchik BL, Lahey A, Cuijpers P, Harrer M,
Jones MT, Nayak SM, Strain EC, Vandekar SN, Dworkin RH, Scott JC, &
Satterthwaite TD. "A living systematic review, meta-analysis and open-data
resource of randomized controlled trials of psilocybin treatment for symptoms
of depression." *Nature Mental Health*, 2026.

**Dataset:** Openly available via `metapsyData::getData("depression-psiloctr")`.
Zenodo DOI: [10.5281/zenodo.17657950](https://zenodo.org/records/17657950).

The analysis applies RoBMA (Maier, Bartoš & Wagenmakers, 2022, *Psychological
Methods*) to the same dataset used by Singleton et al. RoBMA was not used in
the original paper, which assessed publication bias using only Egger's test
(p = 0.21, non-significant) and funnel plot inspection.

Full source code is maintained at: [github.com/metapsy-project/data-depression-psiloctr](https://github.com/metapsy-project/data-depression-psiloctr)

---

## Computational note

RoBMA fits 12 MCMC models per call. Running all 14 analyses from scratch takes
approximately 45–90 minutes depending on hardware. Set `run_fresh <- TRUE` in
the setup chunk to recompute; leave as `FALSE` to load pre-computed results from
`psilodep-robma-results.RData`.

```{r setup, include=FALSE}
run_fresh <- FALSE   # set TRUE to recompute all RoBMA models from scratch

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

---

## Overview

### What RoBMA adds

Singleton et al. (2026) assessed publication bias via Egger's test and funnel
plot inspection, finding no significant asymmetry (intercept = −1.58, p = 0.21).
However, Egger's test has limited power with k = 12 studies and provides no
bias-corrected effect estimate.

RoBMA addresses both gaps by fitting an ensemble of 12 models that jointly vary
across three dimensions:

1. **Effect** — H₀: μ = 0 vs H₁: μ > 0 (Cauchy prior, scale = 0.707)
2. **Heterogeneity** — fixed (τ = 0) vs random (InvGamma(1, 0.15))
3. **Publication bias** — no bias vs four Vevea-Hedges step weight function
   models (one-sided at 0.05; one-sided at 0.05/0.10; two-sided at 0.05;
   two-sided at 0.05/0.10) plus PET-PEESE

Model averaging over these 12 models delivers:

- **BF_effect** — Bayes Factor for effect existing vs not
- **BF_het** — Bayes Factor for between-study heterogeneity
- **BF_pb** — Bayes Factor for publication bias
- **Model-averaged posterior** of μ (pooled effect) and τ (heterogeneity SD),
  corrected for publication bias

### Sign convention

`metapsyTools` outputs negative Hedges' g (negative = psilocybin reduces
depression scores relative to control). RoBMA's default PSMA preset uses a
one-sided prior assuming a positive treatment effect. All effect sizes are
**negated** prior to input (positive g = psilocybin beneficial) and results
are reported in this positive convention throughout.

**Justification for directional prior:** All included trials compared psilocybin
against placebo or inactive control; prior research and mechanism provide a clear
directional expectation that psilocybin reduces depression. A one-sided prior is
therefore appropriate. If the true population effect were negative (psilocybin
worse than control), the PSMA prior would be misspecified — this is an assumption
worth noting, not a decision requiring defence.

### Model-averaging vs model selection

RoBMA does **not** select a single best model. It averages posterior estimates
across all 12 models, weighted by each model's posterior probability. The reported
μ and τ are therefore model-averaged quantities: they integrate uncertainty about
whether publication bias exists, whether effects are heterogeneous, and what the
effect size is — simultaneously. This is distinct from choosing the "winning" model
and reporting its estimates, which would understate total uncertainty.

---

## Load Required Packages

```{r packages}
library(RoBMA)          # v4.0.0 — Robust Bayesian Meta-Analysis
library(metapsyData)    # open dataset access
library(metapsyTools)   # data filtering utilities
library(bayesmeta)      # for comparison with Singleton et al.'s Bayesian analysis
library(dmetar)         # Egger's test (for comparison)
library(tidyverse)
library(ggplot2)
library(patchwork)
library(ggplotify)
```

---

## Data Loading and Quality Checks

The dataset is identical to that used by Singleton et al. (2026). We perform
the same quality checks they report.

```{r load-data}
d    <- getData("depression-psiloctr")
data <- d$data

checkDataFormat(data)
checkConflicts(data,
  vars.for.id = c("study", "outcome_type", "instrument",
                  "study_time_point", "time_weeks", "rating"))
```

---

## Data Preparation and Filtering

We apply the same filtering decisions as Singleton et al.'s primary analysis.
All seven decisions are documented explicitly.

```{r filter-primary}
# Primary analysis dataset — mirrors data_main in Singleton et al.
# Filter decisions:
#   1. Primary instrument per study (prevents double-counting scales)
#   2. Primary timepoint per study (prevents double-counting follow-ups)
#   3. Exclude post-crossover rows (prevents double-counting crossover phases)
#   4. Endpoint data only (msd = mean/SD; imsd = imputed mean/SD)
#   5. Goodwin 2022: exclude 10 mg arm (keep 25 mg vs placebo only)
#   6. Exclude Krempien 2023 (different design; see Singleton et al. methods)
#   7. Exclude Carhart-Harris 2021 (active comparator, not placebo-controlled)

data_main <- data |>
  filterPoolingData(
    primary_instrument == "1",
    primary_timepoint  == "1",
    is.na(post_crossover) | !Detect(post_crossover, "1"),
    outcome_type == "msd" | outcome_type == "imsd",
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm1)) & Detect(multi_arm1, "10 mg")),
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm2)) & Detect(multi_arm2, "10 mg")),
    !Detect(study, "Krempien 2023"),
    !Detect(study, "Carhart-Harris 2021")
  )

cat("Studies in primary analysis:", n_distinct(data_main$study), "\n")
cat("Studies:", paste(sort(unique(data_main$study)), collapse = ", "), "\n")
```

### Subgroup and sensitivity datasets

```{r filter-subgroups}
# Subgroup analyses
data_dep <- data_main |>
  filterPoolingData(diagnosis == "mdd" | diagnosis == "trd")

data_excol <- data_main |>
  filterPoolingData(!Detect(blinding, "open-label"))

data_rob <- data_main |>
  filterPoolingData(!Detect(rob, "High"))

data_parallel <- data_main |>
  filterPoolingData(design == "parallel")

data_crossover <- data_main |>
  filterPoolingData(design == "crossover")

# Sensitivity analyses
data_expanded <- data |>
  filterPoolingData(
    primary_instrument == "1",
    primary_timepoint  == "1",
    outcome_type == "msd" | outcome_type == "imsd",
    !(Detect(study, "Goodwin 2022")  & (!is.na(multi_arm1)) & Detect(multi_arm1, "10 mg")),
    !(Detect(study, "Goodwin 2022")  & (!is.na(multi_arm2)) & Detect(multi_arm2, "10 mg")),
    !(Detect(study, "Krempien 2023") & (!is.na(multi_arm1)) & Detect(multi_arm1, "12 mg")),
    !(Detect(study, "Krempien 2023") & (!is.na(multi_arm2)) & Detect(multi_arm2, "12 mg"))
  )

data_outliers <- data_main |>
  filterPoolingData(!Detect(study, "Davis 2021"))

data_g10 <- data |>
  filterPoolingData(
    primary_instrument == "1",
    primary_timepoint  == "1",
    is.na(post_crossover) | !Detect(post_crossover, "1"),
    outcome_type == "msd" | outcome_type == "imsd",
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm1)) & Detect(multi_arm1, "25 mg")),
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm2)) & Detect(multi_arm2, "25 mg")),
    !Detect(study, "Krempien 2023"),
    !Detect(study, "Carhart-Harris 2021")
  )

data_clinician <- data |>
  filterPoolingData(
    primary_timepoint == "1",
    is.na(post_crossover) | !Detect(post_crossover, "1"),
    !(Detect(study, "Goodwin 2022")     & (!is.na(multi_arm1)) & Detect(multi_arm1, "10 mg")),
    !(Detect(study, "Goodwin 2022")     & (!is.na(multi_arm2)) & Detect(multi_arm2, "10 mg")),
    !Detect(study, "Krempien 2023"),
    !Detect(study, "Carhart-Harris 2021"),
    rating == "clinician",
    Detect(instrument_symptom, "depression"),
    outcome_type != "response",
    outcome_type != "remission",
    outcome_type != "change"
  ) |>
  filterPriorityRule(instrument = c("madrs", "grid-ham-d"))

data_selfreport <- data |>
  filterPoolingData(
    primary_timepoint == "1",
    is.na(post_crossover) | !Detect(post_crossover, "1"),
    !(Detect(study, "Goodwin 2022")     & (!is.na(multi_arm1)) & Detect(multi_arm1, "10 mg")),
    !(Detect(study, "Goodwin 2022")     & (!is.na(multi_arm2)) & Detect(multi_arm2, "10 mg")),
    !Detect(study, "Krempien 2023"),
    !Detect(study, "Carhart-Harris 2021"),
    rating == "self-report",
    Detect(instrument_symptom, "depression"),
    outcome_type != "response",
    outcome_type != "remission",
    outcome_type != "change" & outcome_type != "unknown"
  ) |>
  filterPriorityRule(instrument = c("bdi-ii", "bid-1a", "bdi", "qids-sr",
                                    "hads-d", "smdds", "hads"))

# Dichotomous outcome datasets
data_response <- data |>
  filterPoolingData(
    primary_instrument == "1",
    primary_timepoint  == "1",
    outcome_type       == "response",
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm1)) & Detect(multi_arm1, "10 mg")),
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm2)) & Detect(multi_arm2, "10 mg")),
    !Detect(study, "Krempien 2023")
  )

data_remission <- data |>
  filterPoolingData(
    primary_instrument == "1",
    primary_timepoint  == "1",
    outcome_type       == "remission",
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm1)) & Detect(multi_arm1, "10 mg")),
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm2)) & Detect(multi_arm2, "10 mg")),
    !Detect(study, "Krempien 2023")
  )

# Convenience summary
# Multi-timepoint data for multilevel RoBMA:
# Same as data_main but WITHOUT primary_timepoint == "1",
# so all follow-up timepoints per study are retained (k = 37).
data_time <- data |>
  filterPoolingData(
    primary_instrument == "1",
    is.na(post_crossover) | !Detect(post_crossover, "1"),
    outcome_type == "msd" | outcome_type == "imsd",
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm1)) & Detect(multi_arm1, "10 mg")),
    !(Detect(study, "Goodwin 2022") & (!is.na(multi_arm2)) & Detect(multi_arm2, "10 mg")),
    !Detect(study, "Krempien 2023"),
    !Detect(study, "Carhart-Harris 2021")
  )
cat("data_time: k =", nrow(data_time), "effect sizes from",
    n_distinct(data_time$study), "studies\n")

datasets <- list(
  primary    = data_main,
  dep        = data_dep,
  parallel   = data_parallel,
  crossover  = data_crossover,
  excol      = data_excol,
  rob        = data_rob,
  g10        = data_g10,
  expanded   = data_expanded,
  clinician  = data_clinician,
  selfreport = data_selfreport,
  outliers   = data_outliers
)
purrr::map_int(datasets, \(df) n_distinct(df$study))
```

---

## Helper Functions

```{r helpers}
# Prepare a data_* frame for RoBMA input.
# Negates .g so positive = psilocybin beneficial (required for PSMA prior).
prep_robma <- function(df) {
  df |>
    select(study, .g, .g_se) |>
    filter(!is.na(.g), !is.na(.g_se)) |>
    mutate(g_pos = -.g, g_se = .g_se)
}

# Fit RoBMA with default PSMA preset and study-level effect sizes.
run_robma <- function(df, seed = 4821, sample = 10000, burnin = 4000) {
  RoBMA(
    yi      = df$g_pos,
    sei     = df$g_se,
    slab    = df$study,
    measure = "SMD",
    seed    = seed,
    sample  = sample,
    burnin  = burnin,
    silent  = TRUE
  )
}

# Extract key quantities from a fitted RoBMA object into a one-row tibble.
extract_robma <- function(fit, label, k, pub_g = NA, pub_lo = NA, pub_hi = NA) {
  s    <- summary(fit)
  comp <- s$inclusion_components
  est  <- s$estimates

  bf_effect <- comp$inclusion_BF[1]
  bf_het    <- comp$inclusion_BF[2]
  bf_pb     <- comp$inclusion_BF[3]
  pp_effect <- comp$post_prob[1]
  pp_pb     <- comp$post_prob[3]

  mu_med  <- est[1, "0.5"]
  mu_lo   <- est[1, "0.025"]
  mu_hi   <- est[1, "0.975"]
  tau_med <- est[2, "0.5"]
  mu_ess  <- est[1, "ESS"]
  mu_rhat <- est[1, "R_hat"]

  tibble(
    Analysis    = label,
    k           = k,
    `Pub. g`    = round(pub_g, 2),
    `Pub. CI`   = if (!is.na(pub_lo))
                    sprintf("[%.2f, %.2f]", pub_lo, pub_hi)
                  else NA_character_,
    BF_effect   = round(bf_effect, 2),
    PP_effect   = round(pp_effect, 2),
    BF_pb       = round(bf_pb,     2),
    PP_pb       = round(pp_pb,     2),
    mu_median   = round(mu_med,    2),
    mu_CrI      = sprintf("[%.2f, %.2f]", mu_lo, mu_hi),
    Attenuation = if (!is.na(pub_g) && pub_g != 0)
                    sprintf("%.0f%%", (1 - mu_med / pub_g) * 100)
                  else NA_character_,
    tau_median  = round(tau_med, 2),
    ESS_mu      = round(mu_ess),
    Rhat_mu     = round(mu_rhat, 3)
  )
}
```

---

## RoBMA Analyses

```{r run-or-load}
if (run_fresh) {

  # ── Primary model ────────────────────────────────────────────────────────
  set.seed(4821)
  robma_primary <- run_robma(prep_robma(data_main))

  # ── Subgroup models ──────────────────────────────────────────────────────
  subgroup_datasets <- list(
    dep       = data_dep,
    parallel  = data_parallel,
    crossover = data_crossover,
    excol     = data_excol,
    rob       = data_rob
  )

  robma_subgroups <- purrr::map(subgroup_datasets, \(df) run_robma(prep_robma(df)))

  # ── Sensitivity models ───────────────────────────────────────────────────
  sensitivity_datasets <- list(
    g10        = data_g10,
    expanded   = data_expanded,
    clinician  = data_clinician,
    selfreport = data_selfreport,
    outliers   = data_outliers
  )

  robma_sensitivity <- purrr::map(sensitivity_datasets, \(df) run_robma(prep_robma(df)))

  # ── Dichotomous outcomes ─────────────────────────────────────────────────
  # Run frequentist models first to extract log-RR and SE
  response_results <- runMetaAnalysis(data_response,
    which.run = "overall", es.measure = "RR", es.type = "raw",
    method.tau = "PM", method.tau.ci = "Q-Profile", hakn = TRUE,
    study.var = "study", arm.var.1 = "condition_arm1", arm.var.2 = "condition_arm2",
    measure.var = "instrument", w1.var = "n_arm1", w2.var = "n_arm2",
    time.var = "time_weeks", round.digits = 2)

  remission_results <- runMetaAnalysis(data_remission,
    which.run = "overall", es.measure = "RR", es.type = "raw",
    method.tau = "PM", method.tau.ci = "Q-Profile", hakn = TRUE,
    study.var = "study", arm.var.1 = "condition_arm1", arm.var.2 = "condition_arm2",
    measure.var = "instrument", w1.var = "n_arm1", w2.var = "n_arm2",
    time.var = "time_weeks", round.digits = 2)

  resp_df <- data.frame(
    study = response_results$model.overall$studlab,
    logRR = response_results$model.overall$TE,
    seRR  = response_results$model.overall$seTE)

  remiss_df <- data.frame(
    study = remission_results$model.overall$studlab,
    logRR = remission_results$model.overall$TE,
    seRR  = remission_results$model.overall$seTE)

  robma_response <- RoBMA(yi = resp_df$logRR,   sei = resp_df$seRR,
                          slab = resp_df$study,   measure = "RR",
                          seed = 4821, sample = 10000, burnin = 4000, silent = TRUE)

  robma_remission <- RoBMA(yi = remiss_df$logRR, sei = remiss_df$seRR,
                           slab = remiss_df$study, measure = "RR",
                           seed = 4821, sample = 10000, burnin = 4000, silent = TRUE)

  # ── Prior sensitivity ────────────────────────────────────────────────────
  robma_priors <- list(
    cauchy_05 = RoBMA(yi = prep_robma(data_main)$g_pos,
                      sei = prep_robma(data_main)$g_se,
                      slab = prep_robma(data_main)$study, measure = "SMD",
                      prior_effect = prior(distribution = "Cauchy",
                                           parameters   = list(location = 0, scale = 0.5),
                                           truncation   = list(0, Inf)),
                      seed = 4821, sample = 10000, burnin = 4000, silent = TRUE),

    cauchy_10 = RoBMA(yi = prep_robma(data_main)$g_pos,
                      sei = prep_robma(data_main)$g_se,
                      slab = prep_robma(data_main)$study, measure = "SMD",
                      prior_effect = prior(distribution = "Cauchy",
                                           parameters   = list(location = 0, scale = 1.0),
                                           truncation   = list(0, Inf)),
                      seed = 4821, sample = 10000, burnin = 4000, silent = TRUE),

    normal_01 = RoBMA(yi = prep_robma(data_main)$g_pos,
                      sei = prep_robma(data_main)$g_se,
                      slab = prep_robma(data_main)$study, measure = "SMD",
                      prior_effect = prior(distribution = "normal",
                                           parameters   = list(mean = 0, sd = 1),
                                           truncation   = list(0, Inf)),
                      seed = 4821, sample = 10000, burnin = 4000, silent = TRUE)
  )

  # ── Multilevel RoBMA (k = 37, 12 clusters) ───────────────────────────────
  # RoBMA 4.0.0 cluster argument — Bartoš, Maier & Wagenmakers (2026)
  ml_input_fresh <- data_time |>
    select(study, .g, .g_se) |>
    filter(!is.na(.g), !is.na(.g_se)) |>
    mutate(g_pos = -.g, g_se = .g_se)

  robma_multilevel <- RoBMA(
    yi       = ml_input_fresh$g_pos,
    sei      = ml_input_fresh$g_se,
    cluster  = ml_input_fresh$study,
    measure  = "SMD",
    seed     = 4821,
    sample   = 10000,
    burnin   = 4000,
    parallel = TRUE,
    silent   = TRUE
  )

  # Save all results together in a single call
  save(robma_primary, robma_subgroups, robma_sensitivity,
       robma_response, robma_remission, robma_priors, robma_multilevel,
       file = "psilodep-robma-results.RData")
  cat("All models (including multilevel) saved to psilodep-robma-results.RData\n")

} else {
  load("psilodep-robma-results.RData")
  cat("Pre-computed results loaded from psilodep-robma-results.RData\n")
}
```

---

## Primary RoBMA Results

```{r primary-summary}
summary(robma_primary)
```

The primary RoBMA analysis yields three component Bayes Factors:

- **BF_effect**: evidence for a non-zero pooled effect
- **BF_het**: evidence for between-study heterogeneity
- **BF_pb**: evidence for publication bias

**BF interpretation scale (Jeffreys 1961; Kass & Raftery 1995):**

| BF range | Interpretation |
|---|---|
| 1 – 3 | Anecdotal / not worth more than a mention |
| 3 – 10 | **Moderate** evidence |
| 10 – 30 | Strong evidence |
| > 30 | Very strong / decisive |

BF_pb = 3.90 falls in the moderate range. It meaningfully updates the prior
probability of publication bias from 0.50 to 0.80, but is not decisive. Overstatement
of this finding is a primary risk to guard against.

The model-averaged, bias-corrected posterior for μ should be compared directly
to the published frequentist estimate of g = 0.90 [0.55, 1.26].

**BF_het and the fixed-effects comparison:** BF_het = 1.75 constitutes only
anecdotal evidence for heterogeneity. This is consistent with the original
fixed-effects model (g = 0.84 [1.02, 0.67]), which was nearly identical to
the REML random-effects estimate (g = 0.90). RoBMA's internal comparison of
fixed vs random models captures what the original FE sensitivity analysis showed
— without requiring a separate model fit.

```{r primary-posterior-plot}
plot(robma_primary, parameter = "mu", prior = TRUE,
     main = "Posterior of μ (model-averaged) vs prior")
abline(v = 0.90, col = "firebrick", lty = 2, lwd = 1.5)
legend("topleft", legend = "Published g = 0.90 (Singleton et al., 2026)",
       col = "firebrick", lty = 2, bty = "n", cex = 0.85)
```

```{r primary-weightfunction}
plot(robma_primary, parameter = "weightfunction",
     main = "Model-averaged publication bias weight function (ω)")
```

**Weight function interpretation:** All ω posterior medians sit at 1.0 (maximum
publication probability), with credible intervals extending down to ~0.19–0.44 for
the non-significant p-value ranges. This does not mean "no bias" — it means the
data are consistent with either no bias or moderate bias, and the model averaging
(BF_pb = 3.90) is what shifts the posterior toward bias being present. The diffuse
ω posteriors indicate that the specific *form* of bias is uncertain; the model
averages over all specified weight function shapes.

**PET and PEESE posteriors:** Both are centred near zero (PET median ≈ 0,
PEESE median ≈ 0), with wide credible intervals. This indicates that neither
funnel-plot-based bias mechanism is individually supported — bias evidence in the
primary model comes from the weight function models, not from PET-PEESE. This is
an important nuance for the manuscript: BF_pb is not driven by a simple
small-study effect.

### Comparison with Egger's test

```{r egger-comparison}
# Singleton et al.'s original publication bias assessment used Egger's test
# Re-run frequentist primary model for Egger's test comparison
main_results_freq <- runMetaAnalysis(data_main,
  which.run = "overall", es.measure = "g", method.tau = "REML",
  method.tau.ci = "Q-Profile", hakn = TRUE,
  study.var = "study", arm.var.1 = "condition_arm1", arm.var.2 = "condition_arm2",
  measure.var = "instrument", w1.var = "n_arm1", w2.var = "n_arm2",
  time.var = "time_weeks", round.digits = 2)

eggers.test(main_results_freq$model.overall)

cat("\nEgger's test: p = 0.21 (non-significant with k = 12)\n")
cat("RoBMA BF_pb =", round(summary(robma_primary)$inclusion_components$inclusion_BF[3], 2),
    "(posterior probability =",
    round(summary(robma_primary)$inclusion_components$post_prob[3], 2), ")\n")
cat("\nNote: Egger's test has low power at k = 12.\n",
    "RoBMA's model-averaging approach is more sensitive to weak bias signals.\n")
```

---

## Prior Sensitivity Analysis

We test three alternative effect priors to verify that conclusions about
publication bias (BF_pb) and the bias-corrected effect (μ) are not
driven by the default Cauchy(0, 0.707) specification.

```{r prior-sensitivity-table}
extract_prior <- function(fit, label) {
  s    <- summary(fit)
  comp <- s$inclusion_components
  est  <- s$estimates
  tibble(
    Prior       = label,
    BF_effect   = round(comp$inclusion_BF[1], 2),
    PP_effect   = round(comp$post_prob[1],    2),
    BF_pb       = round(comp$inclusion_BF[3], 2),
    PP_pb       = round(comp$post_prob[3],    2),
    mu_median   = round(est[1, "0.5"],        2),
    mu_CrI      = sprintf("[%.2f, %.2f]", est[1, "0.025"], est[1, "0.975"]),
    ESS_mu      = round(est[1, "ESS"])
  )
}

prior_table <- bind_rows(
  extract_prior(robma_primary,          "Cauchy(0, 0.707) — default PSMA"),
  extract_prior(robma_priors$cauchy_05, "Cauchy(0, 0.5)   — conservative"),
  extract_prior(robma_priors$cauchy_10, "Cauchy(0, 1.0)   — diffuse"),
  extract_prior(robma_priors$normal_01, "Normal(0, 1)     — matches bayesmeta (Singleton et al.)")
)

prior_table
```

BF_pb ranges `r round(min(prior_table$BF_pb), 2)`–`r round(max(prior_table$BF_pb), 2)` and μ median ranges `r round(min(prior_table$mu_median), 2)`–`r round(max(prior_table$mu_median), 2)` across all four priors. Conclusions are robust to prior specification.

**Heterogeneity prior:** The default InvGamma(1, 0.15) prior for τ places most
mass below τ = 1, which is reasonable for standardised effect size differences.
An alternative InvGamma(1, 0.25) (more diffuse) was considered but not separately
run; given that BF_het = 1.75 (weak evidence for heterogeneity) and τ posteriors
are dominated by the data at k = 12, heterogeneity prior sensitivity is expected
to be lower than effect prior sensitivity and is not a primary concern here.

---

## Subgroup Analyses

Each subgroup mirrors a corresponding analysis in Singleton et al. (2026).
⚠ marks analyses with k < 8; BF_pb is highly prior-dependent at small k and
should be interpreted with caution.

```{r subgroup-results}
pub_vals <- list(
  dep       = c(g = 0.93, lo = 0.00, hi = 1.87),
  parallel  = c(g = 0.80, lo = 0.49, hi = 1.11),
  crossover = c(g = 1.04, lo = 0.03, hi = 2.06),
  excol     = c(g = 0.81, lo = 0.60, hi = 1.03),
  rob       = c(g = 0.97, lo = 0.57, hi = 1.38)
)

labels <- list(
  dep       = "MDD/TRD diagnosis (k=5) ⚠",
  parallel  = "Parallel design (k=7)",
  crossover = "Crossover only (k=5) ⚠",
  excol     = "Excl. open-label (k=9)",
  rob       = "Excl. high RoB (k=9)"
)

subgroup_table <- purrr::imap_dfr(robma_subgroups, \(fit, nm) {
  k   <- n_distinct(datasets[[nm]]$study)
  pv  <- pub_vals[[nm]]
  extract_robma(fit, labels[[nm]], k, pv["g"], pv["lo"], pv["hi"])
})

subgroup_table |>
  select(Analysis, k, `Pub. g`, BF_effect, BF_pb, mu_median, mu_CrI, Attenuation)
```

### Key subgroup finding: open-label studies drive the bias signal

```{r open-label-comparison}
cat("Publication bias Bayes Factors by design:\n\n")
cat(sprintf("  Excl. open-label (k=9): BF_pb = %.2f  → no bias evidence\n",
    subgroup_table$BF_pb[subgroup_table$Analysis == "Excl. open-label (k=9)"]))
cat(sprintf("  Parallel design  (k=7): BF_pb = %.2f  → minimal bias evidence\n",
    subgroup_table$BF_pb[subgroup_table$Analysis == "Parallel design (k=7)"]))
cat(sprintf("  Primary model   (k=12): BF_pb = %.2f  → moderate bias evidence\n",
    summary(robma_primary)$inclusion_components$inclusion_BF[3]))
cat("\nInterpretation: When open-label and crossover studies are removed,\n")
cat("publication bias evidence largely disappears. The bias signal in the\n")
cat("primary model appears driven by open-label designs — consistent with\n")
cat("the functional unblinding concern rather than file-drawer suppression\n")
cat("of blinded RCTs.\n")
```

---

## Sensitivity Analyses

```{r sensitivity-results}
pub_vals_sens <- list(
  g10        = c(g = 0.87, lo = 0.47, hi = 1.27),
  expanded   = c(g = 0.88, lo = 0.56, hi = 1.21),
  clinician  = c(g = 1.02, lo = 0.44, hi = 1.60),
  selfreport = c(g = 1.00, lo = 0.31, hi = 1.68),
  outliers   = c(g = 0.81, lo = 0.55, hi = 1.07)
)

labels_sens <- list(
  g10        = "Goodwin 10 mg arm (k=12)",
  expanded   = "Expanded inclusion (k=15)",
  clinician  = "Clinician-rated (k=7)",
  selfreport = "Self-report (k=9) †",
  outliers   = "Excl. Davis 2021 (k=11)"
)

datasets_sens <- list(
  g10        = data_g10,
  expanded   = data_expanded,
  clinician  = data_clinician,
  selfreport = data_selfreport,
  outliers   = data_outliers
)

sensitivity_table <- purrr::imap_dfr(robma_sensitivity, \(fit, nm) {
  k   <- n_distinct(datasets_sens[[nm]]$study)
  pv  <- pub_vals_sens[[nm]]
  extract_robma(fit, labels_sens[[nm]], k, pv["g"], pv["lo"], pv["hi"])
})

sensitivity_table |>
  select(Analysis, k, `Pub. g`, BF_effect, BF_pb, mu_median, mu_CrI, Attenuation)
```

**† Self-report BF_pb = `r sensitivity_table$BF_pb[grepl("Self-report", sensitivity_table$Analysis)]`:**
This is a degenerate or near-degenerate estimate. With k = 9 and I² = 73%, the
weight function models become numerically extreme. Do not report at face value;
treat as "BF_pb ≫ 100, unreliable" in any summary table.

**Goodwin 10 mg (BF_pb = `r sensitivity_table$BF_pb[grepl("Goodwin", sensitivity_table$Analysis)]`):**
Using the 10 mg arm (genuinely lower dose-response) conflates lower efficacy
with publication bias. Interpret with caution; not straightforwardly comparable
to the primary model.

**Davis 2021 (Excl. Davis 2021: BF_pb = `r sensitivity_table$BF_pb[grepl("Davis", sensitivity_table$Analysis)]`):**
When the outlier (g = 2.48) is excluded, publication bias evidence drops to
near-zero. Davis 2021 appears to be a secondary driver of the bias signal.

---

## Dichotomous Outcomes

```{r dichotomous-results}
# Summarise
extract_dich <- function(fit, label, k, pub_RR, pub_lo, pub_hi) {
  s    <- summary(fit)
  comp <- s$inclusion_components
  est  <- s$estimates
  mu   <- est[1, "0.5"]
  tibble(
    Analysis    = label, k = k,
    `Pub. RR`   = round(pub_RR, 2),
    `Pub. CI`   = sprintf("[%.2f, %.2f]", pub_lo, pub_hi),
    BF_effect   = round(comp$inclusion_BF[1], 2),
    BF_pb       = round(comp$inclusion_BF[3], 2),
    `RoBMA RR`  = round(exp(mu), 2),
    `RoBMA CrI` = sprintf("[%.2f, %.2f]",
                          exp(est[1, "0.025"]), exp(est[1, "0.975"])),
    Attenuation = sprintf("%.0f%%", (1 - exp(mu) / pub_RR) * 100),
    ESS_mu      = round(est[1, "ESS"])
  )
}

dich_table <- bind_rows(
  extract_dich(robma_response,  "Response (k=5) ⚠",  5, 2.77, 1.93, 3.97),
  extract_dich(robma_remission, "Remission (k=6) ⚠", 6, 4.04, 3.39, 4.82)
)

dich_table
```

Both dichotomous outcomes show modest attenuation (17% and 21%) relative to
published risk ratios. The effect remains clearly positive for remission
(BF_effect = `r dich_table$BF_effect[2]`) with weaker publication bias evidence
(BF_pb = `r dich_table$BF_pb[2]`). ⚠ k = 5–6; bias estimation has limited power.

**Fixed-effects dichotomous sensitivity (1.5.3):** Singleton et al. ran FE
sensitivity models for both response and remission (both I² = 0%, so FE and RE
estimates are identical). RoBMA captures this internally via BF_het — both
dichotomous analyses return BF_het near 1 and τ ≈ 0, confirming that fixed vs
random effects makes no practical difference here. No separate RoBMA run is needed.

---

## Comprehensive Results Table (Extended Data Table 1)

This table mirrors the TODO's "Extended Data Figure 2: Subgroup & Sensitivity
RoBMA" — all primary, subgroup, and sensitivity analyses in one place.
Flagged analyses (⚠) have k < 8; BF_pb is highly prior-dependent at small k.
Degenerate analyses (†) should not be reported at face value.

```{r full-results-table}
pub_primary <- c(g = 0.90, lo = 0.55, hi = 1.26)

results_table <- bind_rows(
  extract_robma(robma_primary, "Primary (k=12)", 12,
                pub_primary["g"], pub_primary["lo"], pub_primary["hi"]),
  subgroup_table,
  sensitivity_table
)

results_table |>
  select(Analysis, k, `Pub. g`, `Pub. CI`, BF_effect, PP_effect,
         BF_pb, PP_pb, mu_median, mu_CrI, Attenuation, ESS_mu, Rhat_mu) |>
  print(n = Inf, width = Inf)
```

```{r save-ed-table}
# Save the comprehensive table as a formatted CSV for the submission package
results_table |>
  select(Analysis, k, `Pub. g`, `Pub. CI`, BF_effect, PP_effect,
         BF_pb, PP_pb, mu_median, mu_CrI, Attenuation, ESS_mu, Rhat_mu) |>
  write.csv("ED_Table1_comprehensive_results.csv", row.names = FALSE)
cat("Extended Data Table 1 saved to ED_Table1_comprehensive_results.csv\n")
```

---

## MCMC Diagnostics

All models must satisfy R-hat ≤ 1.01 and ESS_μ > 400 for results to be
trustworthy. ⚠ flags borderline values.

```{r mcmc-diagnostics}
diag_table <- purrr::imap_dfr(
  c(list(primary = robma_primary),
    robma_subgroups,
    robma_sensitivity,
    list(response = robma_response, remission = robma_remission,
         multilevel = robma_multilevel)),
  \(fit, nm) {
    est <- summary(fit)$estimates
    tibble(
      Model    = nm,
      ESS_mu   = round(est[1, "ESS"]),
      ESS_tau  = round(est[2, "ESS"]),
      Rhat_mu  = round(est[1, "R_hat"], 3),
      Rhat_tau = round(est[2, "R_hat"], 3),
      Flag     = if_else(est[1, "R_hat"] > 1.01 | est[1, "ESS"] < 400, "⚠", "✓")
    )
  }
)

diag_table
```

---

## Figures

### Figure 1 (main): Three-panel comparison

```{r figure-1, fig.width=10, fig.height=10}
# ── Panel A: posterior of μ vs prior ─────────────────────────────────────────
# TODO called for BF_effect and BF_pb to be annotated directly on panel A.
# In the final figure these are reported in the figure caption and in panel C's
# BF_pb column rather than as text overlays on panel A, to avoid crowding the
# density plot. The caption reads: "a: dashed = published g = 0.90; BF_effect =
# 3.68, BF_pb = 3.90 (primary model)."
#
# Captured via pdf() — RoBMA's plot() opens an internal graphics device that
# desynchronises the png() capture stack. pdf() is file-based and immune.
tmp_pdf_A <- tempfile(fileext = ".pdf")
pdf(tmp_pdf_A, width = 5.5, height = 4.5)
par(mar = c(5, 5, 3, 6))  # mar[4] = 6 to clear the right y-axis labels
plot(robma_primary, parameter = "mu", prior = TRUE,
     main = expression(bold("a") ~~ "Posterior of" ~ mu ~ "vs prior"))
abline(v = 0.90, col = "firebrick", lty = 2, lwd = 1.8)
usr <- par("usr")
text(x = 0.95, y = usr[4] * 0.70,
     "Published\ng = 0.90", col = "firebrick", adj = 0, cex = 0.82)
invisible(dev.off())
magick::image_write(magick::image_read_pdf(tmp_pdf_A, density = 300),
                    "tmp_pA.png", format = "png")

# ── Panel B: ω posteriors (ggplot2 — immune to device conflicts) ─────────────
bias_est <- summary(robma_primary)$estimates_bias
omega_df <- data.frame(
  interval = c("(0.025,\n0.05]", "(0.05,\n0.5]", "(0.5,\n0.95]",
                "(0.95,\n0.975]", "(0.975,\n1]"),
  median   = bias_est[2:6, "0.5"],
  lo       = bias_est[2:6, "0.025"],
  hi       = bias_est[2:6, "0.975"]
) |> mutate(interval = factor(interval, levels = interval))

pB_plot <- ggplot(omega_df, aes(x = interval, y = median)) +
  geom_hline(yintercept = 1, linetype = "dashed", colour = "grey60") +
  geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.18,
                colour = "grey40", linewidth = 0.7) +
  geom_point(size = 3.5, colour = "#1f4e79") +
  scale_y_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.25),
                     name = expression(omega ~ "posterior median [95% CrI]")) +
  labs(x = "One-sided p-value interval",
       title = expression(bold("b") ~~ "Weight function (" * omega * ")"),
       subtitle = "Dashed = \u03c9 = 1 (no selection)") +
  theme_classic(base_size = 11) +
  theme(plot.title    = element_text(size = 10, face = "bold"),
        plot.subtitle = element_text(size = 8.5, colour = "grey45"),
        axis.text.x   = element_text(size = 8))
ggsave("tmp_pB.png", pB_plot, width = 5, height = 4.5, dpi = 300)

# ── Panel C: comparison forest ───────────────────────────────────────────────
# Single-level rows (warning flags derived from k)
base_rows <- results_table |>
  filter(!grepl("Self-report|Goodwin 10 mg|Crossover", Analysis)) |>
  mutate(
    Analysis = str_remove(Analysis, " \u26a0$"),
    Analysis = if_else(k < 8, paste0(Analysis, " \u26a0"), Analysis),
    pub_lo   = c(0.55, 0.00, 0.49, 0.60, 0.57, 0.56, 0.44, 0.55),
    pub_hi   = c(1.26, 1.87, 1.11, 1.03, 1.38, 1.21, 1.60, 1.07),
    mu_lo_n  = as.numeric(str_extract(mu_CrI, "-?[0-9.]+")),
    mu_hi_n  = as.numeric(str_extract(mu_CrI, "(?<=, )-?[0-9.]+"))
  ) |>
  select(Analysis, k, `Pub. g`, pub_lo, pub_hi, BF_pb, mu_median, mu_lo_n, mu_hi_n)

# Multilevel row — published comparison is the CHE model (Singleton et al.)
ml_row <- tibble(
  Analysis  = "Multilevel RoBMA (k=37) \u2020",
  k         = 37L,
  `Pub. g`  = 0.82,  # CHE estimate (positive convention)
  pub_lo    = 0.57, pub_hi = 1.08,
  BF_pb     = 28.27,
  mu_median = 0.00,
  mu_lo_n   = -0.15, mu_hi_n = 0.77
)

# Combine: multilevel at bottom (row = 1), single-level rows 2–9
all_labels <- c(rev(base_rows$Analysis), "Multilevel RoBMA (k=37) \u2020")
forest_df  <- bind_rows(base_rows, ml_row) |>
  mutate(Analysis = factor(Analysis, levels = rev(all_labels)),
         row      = as.integer(Analysis))

pC_plot <- ggplot(forest_df) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  # Dotted separator between multilevel and single-level rows
  geom_hline(yintercept = 1.55, linetype = "dotted",
             colour = "grey60", linewidth = 0.4) +
  geom_errorbar(aes(xmin = pub_lo, xmax = pub_hi, y = row + 0.2),
                width = 0.15, colour = "#1f4e79", linewidth = 0.6,
                orientation = "y") +
  geom_point(aes(x = `Pub. g`, y = row + 0.2), shape = 16, size = 2.8,
             colour = "#1f4e79") +
  geom_errorbar(aes(xmin = mu_lo_n, xmax = mu_hi_n, y = row - 0.2),
                width = 0.15, colour = "#c55a11", linewidth = 0.6,
                orientation = "y") +
  geom_point(aes(x = mu_median, y = row - 0.2), shape = 15, size = 2.8,
             colour = "#c55a11") +
  geom_text(aes(x = 1.85, y = row,
                label = sprintf("BF[pb]==%.2f", BF_pb)),
            parse = TRUE, size = 2.8, hjust = 0, colour = "grey30") +
  scale_y_continuous(breaks = forest_df$row, labels = forest_df$Analysis,
                     limits = c(0.5, 9.6)) +
  scale_x_continuous(limits = c(-0.3, 2.3), breaks = seq(0, 2, 0.5),
                     name = "Effect size (Hedges' g)") +
  labs(y = NULL,
       subtitle = "Navy \u25cf = published [95% CI];  Orange \u25a0 = RoBMA bias-corrected [95% CrI]") +
  theme_classic(base_size = 11) +
  theme(axis.text.y   = element_text(size = 8.5),
        plot.subtitle = element_text(size = 9, colour = "grey40"))
ggsave("tmp_pC.png", pC_plot, width = 10, height = 7, dpi = 300)

# ── Compose with magick ───────────────────────────────────────────────────────
img_A  <- magick::image_read("tmp_pA.png")
img_B  <- magick::image_read("tmp_pB.png")
h_max  <- max(magick::image_info(img_A)$height, magick::image_info(img_B)$height)
top    <- magick::image_append(
  c(magick::image_resize(img_A, paste0("x", h_max)),
    magick::image_resize(img_B, paste0("x", h_max))))
bottom <- magick::image_read("tmp_pC.png")
w      <- magick::image_info(bottom)$width
cap    <- magick::image_blank(w, 160, color = "white") |>
  magick::image_annotate(
    # Plain ASCII only — Unicode subscripts and special symbols do not render
    # reliably in magick's system font pipeline.
    # Two-line caption with \n to prevent right-edge clipping.
    paste0(
      "a: posterior of mu (black) vs prior (grey); dashed = published g = 0.90 (Singleton et al. 2026); ",
      "primary model: BF_effect = 3.68, BF_pb = 3.90.\n",
      "b: omega posterior median [95% CrI] per p-value interval; dashed = omega = 1 (no selection).\n",
      "c: BF_pb per row. Triangle = k < 8; interpret BF_pb cautiously. ",
      "Dagger (dagger) = multilevel RoBMA (k = 37 effect sizes, 12 study clusters); ",
      "published = CHE model estimate (Singleton et al.); within-study selection caveat applies."
    ),
    size = 24, color = "grey45", gravity = "NorthWest", location = "+20+12")
fig1_composed <- magick::image_append(
  c(magick::image_scale(top, paste0(w, "x")), bottom, cap), stack = TRUE)
magick::image_write(fig1_composed, "fig1_robma_main.jpg",
                    format = "jpeg", quality = 95)
file.remove(c("tmp_pA.png", "tmp_pB.png", "tmp_pC.png"))
cat("Figure 1 saved:", magick::image_info(fig1_composed)$width, "x",
    magick::image_info(fig1_composed)$height, "px\n")
```

### Extended Data Figure 1: Prior sensitivity

```{r ed-fig1, fig.width=9, fig.height=4.5}
prior_plot_df <- prior_table |>
  mutate(Prior = factor(Prior, levels = rev(Prior)),
         row   = as.integer(Prior))

ed1 <- ggplot(prior_plot_df) +
  geom_point(aes(x = mu_median, y = row), shape = 18, size = 4,
             colour = "#c55a11") +
  geom_errorbar(aes(
    xmin = as.numeric(str_extract(mu_CrI, "-?[0-9.]+")),
    xmax = as.numeric(str_extract(mu_CrI, "(?<=, )-?[0-9.]+")),
    y = row), width = 0.2, colour = "#c55a11", linewidth = 0.7,
    orientation = "y") +
  geom_text(aes(x = 1.25, y = row,
                label = sprintf("BF[effect]==%.2f~~BF[pb]==%.2f",
                                BF_effect, BF_pb)),
            parse = TRUE, size = 3.2, hjust = 0) +
  geom_vline(xintercept = 0,    linetype = "dashed", colour = "grey60") +
  geom_vline(xintercept = 0.53, linetype = "dotted", colour = "#c55a11", alpha = 0.5) +
  scale_y_continuous(breaks = prior_plot_df$row, labels = prior_plot_df$Prior) +
  scale_x_continuous(limits = c(-0.1, 2.2), breaks = seq(0, 2, 0.5)) +
  labs(x = "RoBMA μ median [95% CrI]", y = NULL,
       title = "Extended Data Fig. 1 — Prior sensitivity analysis",
       subtitle = "Dotted vertical = default PSMA estimate (μ = 0.53)") +
  theme_classic(base_size = 11) +
  theme(plot.title    = element_text(face = "bold", size = 11),
        plot.subtitle = element_text(size = 8.5, colour = "grey40"),
        axis.text.y   = element_text(size = 9))

ed1
ggsave("fig_ED1_prior_sensitivity.jpg", ed1, width = 9, height = 4.5, dpi = 300)
```

### Extended Data Figure 2: Dichotomous outcomes

```{r ed-fig2, fig.width=9, fig.height=3.8}
dich_plot_df <- dich_table |>
  mutate(Analysis = factor(Analysis, levels = rev(Analysis)),
         row = as.integer(Analysis),
         pub_lo = c(1.93, 3.39), pub_hi = c(3.97, 4.82),
         mu_lo  = as.numeric(str_extract(`RoBMA CrI`, "[0-9.]+")),
         mu_hi  = as.numeric(str_extract(`RoBMA CrI`, "(?<=, )[0-9.]+")))

# Add BF_pb values directly — avoid \uxxxx inside backtick names (knitr parser error)
dich_plot_df2 <- dich_plot_df |>
  mutate(BF_pb = case_when(
    grepl("Response",  as.character(Analysis)) ~ 3.40,
    grepl("Remission", as.character(Analysis)) ~ 2.24,
    TRUE ~ NA_real_
  ))

ed2 <- ggplot(dich_plot_df2) +
  geom_vline(xintercept = 1, linetype = "dashed", colour = "grey60") +
  geom_errorbar(aes(xmin = pub_lo, xmax = pub_hi, y = row + 0.2),
                width = 0.12, colour = "#1f4e79", linewidth = 0.7,
                orientation = "y") +
  geom_point(aes(x = `Pub. RR`, y = row + 0.2), shape = 16, size = 3,
             colour = "#1f4e79") +
  geom_errorbar(aes(xmin = mu_lo, xmax = mu_hi, y = row - 0.2),
                width = 0.12, colour = "#c55a11", linewidth = 0.7,
                orientation = "y") +
  geom_point(aes(x = `RoBMA RR`, y = row - 0.2), shape = 15, size = 3,
             colour = "#c55a11") +
  # BF_pb annotation — mirrors style of panel c in Fig. 1
  geom_text(aes(x = 7.2, y = row,
                label = sprintf("BF[pb]==%.2f", BF_pb)),
            parse = TRUE, size = 3.2, hjust = 0, colour = "grey30") +
  scale_y_continuous(breaks = dich_plot_df2$row,
                     labels = dich_plot_df2$Analysis) +
  scale_x_continuous(limits = c(0.5, 9.2), breaks = 1:6,
                     name = "Risk Ratio") +
  labs(
    y        = NULL,
    title    = "Extended Data Fig. 2 \u2014 Dichotomous outcomes",
    subtitle = "Navy \u25cf = published [95% CI];  Orange \u25a0 = RoBMA bias-corrected [95% CrI]",
    # Avoid \u26a0 — may not have JPEG font glyphs; ggplot2 renders it as △
    caption  = "Triangle = k < 8; BF_pb has limited power and should be interpreted cautiously."
  ) +
  theme_classic(base_size = 11) +
  theme(
    plot.title    = element_text(face = "bold", size = 11),
    plot.subtitle = element_text(size = 8.5, colour = "grey40"),
    plot.caption  = element_text(size = 8,   colour = "grey45", hjust = 0)
  )

ed2
ggsave("fig_ED2_dichotomous.jpg", ed2, width = 9, height = 3.8, dpi = 300)
```

### Extended Data Figure 3: MCMC diagnostics

```{r ed-fig3}
diag_table |> print(n = Inf)
```

---

## Scope Limitations

The following analyses from Singleton et al. (2026) are **outside RoBMA's scope**
and are not replicated here. Each is addressed in the manuscript's Methods or Discussion.

| Analysis in Singleton et al. | RoBMA status | Reason |
|---|---|---|
| Three-level CHE model (k = 37) | **Replicated and extended** — see Multilevel RoBMA section below | RoBMA 4.0 `cluster` argument implements compound-symmetric structure (Bartoš, Maier & Wagenmakers, 2026); adds publication bias correction |
| Rho sensitivity sweep | Not replicated | Specific to CHE; not applicable to RoBMA |
| Meta-regression on time_days | Not replicated | Out of scope; β = 0.0019/day (p = 0.17) in original suggests no decay |
| Design moderation test | Partial | Parallel/crossover RoBMA runs serve as substitute |
| Fixed-effects model | Captured internally | RoBMA models fixed effects via BF_het component |
| bayesmeta sensitivity | Superseded | RoBMA extends bayesmeta by adding publication bias correction |

---

## Multilevel RoBMA (Extending the CHE Model)

RoBMA 4.0.0 supports multilevel (clustered) meta-analysis via the `cluster`
argument, implementing the same compound-symmetric structure as the three-level
CHE model in Singleton et al. (Bartoš, Maier & Wagenmakers, 2026, *Behavior
Research Methods*). This allows publication bias correction across the full
k = 37 effect sizes from 12 studies, partitioning heterogeneity into
within-study (τ_within, across timepoints) and between-study (τ_between)
components simultaneously with bias adjustment.

**Important methodological caveat:** Standard publication bias selection models
assume that each effect size could, in principle, be an unpublished study.
Within-study effect sizes from different timepoints are all from the same
*published* paper — there is no traditional within-study publication selection.
The weight functions in the multilevel model therefore target study-level bias,
but the PEESE component may conflate within-study timepoint heterogeneity with
funnel plot asymmetry. Interpret with this in mind; the single-level primary
RoBMA (using one effect size per study) remains the most methodologically
straightforward analysis for publication bias detection.

```{r multilevel-data}
# Multi-timepoint data: same studies as primary, all timepoints retained
# data_time contains k = 37 effect sizes from 12 studies (1-6 per study)
ml_input <- data_time |>
  select(study, .g, .g_se) |>
  filter(!is.na(.g), !is.na(.g_se)) |>
  mutate(g_pos = -.g, g_se = .g_se)  # negate: positive = psilocybin beneficial

ml_input |>
  group_by(study) |>
  summarise(n_timepoints = n(), .groups = "drop") |>
  arrange(desc(n_timepoints))
```

```{r multilevel-robma-note}
# robma_multilevel is fitted in the main run-or-load chunk (run_fresh = TRUE)
# or loaded from psilodep-robma-results.RData (run_fresh = FALSE).
# Both paths produce the same object; no separate fitting call is needed here.
cat("robma_multilevel loaded:", inherits(robma_multilevel, "RoBMA"), "\n")
cat("k =", nrow(ml_input), "| clusters =", n_distinct(ml_input$study), "\n")
```

```{r multilevel-results}
summary(robma_multilevel)
```

```{r multilevel-heterogeneity}
# Heterogeneity decomposition: within- vs between-study
summary_heterogeneity(robma_multilevel)
```

**Results interpretation:**

```{r multilevel-comparison}
s_ml <- summary(robma_multilevel)
cat("── Multilevel RoBMA vs CHE model (Singleton et al.) ─────────────\n\n")

cat("CHE (frequentist, no bias correction):\n")
cat("  μ = 0.82 [0.57, 1.08]\n")
cat("  τ_between = 0.287, τ_within = 0.212\n\n")

cat("Multilevel RoBMA (bias-corrected, same 37 effect sizes):\n")
cat(sprintf("  μ median = %.2f [%.2f, %.2f]\n",
            s_ml$estimates["mu","0.5"],
            s_ml$estimates["mu","0.025"],
            s_ml$estimates["mu","0.975"]))
cat(sprintf("  BF_effect = %.2f  (posterior prob = %.2f)\n",
            s_ml$inclusion_components$inclusion_BF[1],
            s_ml$inclusion_components$post_prob[1]))
cat(sprintf("  BF_het    = %.2f  (posterior prob = %.2f)\n",
            s_ml$inclusion_components$inclusion_BF[2],
            s_ml$inclusion_components$post_prob[2]))
cat(sprintf("  BF_pb     = %.2f  (posterior prob = %.2f)\n",
            s_ml$inclusion_components$inclusion_BF[3],
            s_ml$inclusion_components$post_prob[3]))
cat(sprintf("  ESS_mu    = %d  R-hat = %.3f\n",
            round(s_ml$estimates["mu","ESS"]),
            s_ml$estimates["mu","R_hat"]))
cat("\n⚠ ESS_mu = 279 (below target of 1000). Estimates for mu are\n")
cat("  less stable than the primary model; interpret with caution.\n")
cat("  The BF_pb and heterogeneity components are well-sampled (ESS > 2000).\n\n")

cat("Heterogeneity decomposition:\n")
het    <- summary_heterogeneity(robma_multilevel)
het_df <- het$estimates   # data.frame: rows = parameters, cols = Mean/Median/0.025/0.975
cat(sprintf("  τ_total   = %.3f [%.3f, %.3f]\n",
            het_df["tau",        "Median"], het_df["tau",        "0.025"], het_df["tau",        "0.975"]))
cat(sprintf("  τ_between = %.3f [%.3f, %.3f]  (between studies)\n",
            het_df["tau [between]","Median"], het_df["tau [between]","0.025"], het_df["tau [between]","0.975"]))
cat(sprintf("  τ_within  = %.3f [%.3f, %.3f]  (within studies, across timepoints)\n",
            het_df["tau [within]", "Median"], het_df["tau [within]", "0.025"], het_df["tau [within]", "0.975"]))
cat(sprintf("  ρ (between allocation) = %.3f [%.3f, %.3f]\n",
            het_df["rho",        "Median"], het_df["rho",        "0.025"], het_df["rho",        "0.975"]))
```

**Key findings from multilevel RoBMA:**

1. **BF_pb = 28.27** (strong evidence) — substantially higher than the single-level
   primary model (BF_pb = 3.90). When the full multi-timepoint structure is modelled,
   publication bias evidence is much clearer.

2. **μ median = 0.00 [−0.15, 0.77]** — The bias-corrected effect collapses to near
   zero, compared to g = 0.82 in the CHE model. The credible interval is very wide,
   spanning negative to moderately positive values. This reflects high uncertainty,
   not a definitive null finding.

3. **BF_effect = 0.84** (weak evidence against effect) — In contrast to the
   single-level primary model (BF_effect = 3.68, moderate evidence for effect).

4. **ρ = 0.80** — Most heterogeneity is between studies rather than within studies
   across timepoints, consistent with the CHE model's σ²_between > σ²_within.

5. **PEESE mean = 3.34 [0, 7.57]** — Active PEESE component; caution warranted
   given the within-study interpretation issue noted above.

---

**What RoBMA cannot correct regardless of results:**

- **Functional unblinding:** psilocybin produces unmistakable subjective effects;
  participants in every trial knew their allocation. Expectancy effects are not
  modeled by weight functions. This is the most important limitation — it is
  independent of publication bias and cannot be statistically corrected.
- **Selective outcome reporting *within* studies:** RoBMA's weight function
  mechanism models suppression of whole studies, not suppression of unfavorable
  outcomes within published studies.
- **Selective timepoint reporting:** The CHE model in Singleton et al. addressed
  within-study correlation across multiple follow-up timepoints. RoBMA uses only
  one effect size per study (primary timepoint), meaning that if investigators
  selectively reported favorable timepoints *within* studies, this form of bias
  is not captured.
- **Primary instrument/timepoint selection as researcher degrees of freedom:**
  The rules used to select the primary instrument and timepoint per study are
  themselves analytical decisions. RoBMA treats the selected effect sizes as
  given and does not model uncertainty arising from this upstream selection step.
- **Setting dependency:** All trials used structured therapeutic protocols
  (preparation, monitored dosing, integration). Effect sizes reflect
  psilocybin + therapy, not the molecule alone.
- **Heterogeneous populations:** Studies include MDD, TRD, cancer-related
  depression, and palliative care populations. RoBMA pools across these without
  moderation, which the subgroup analyses partially address.
- **Heterogeneous comparators:** Control conditions include placebo, niacin,
  microcrystalline cellulose, and active placebos. Variation in comparator
  inertness affects absolute effect size estimates; RoBMA does not model this.

**Exclusion decisions inherited from Singleton et al.:**

- *Carhart-Harris 2021* excluded: used an active comparator (escitalopram) rather
  than placebo, making the effect size metric non-comparable to placebo-controlled
  trials. This exclusion is well-justified and does not bias our RoBMA.
- *Grob 2011* excluded: a pilot study in cancer patients with life-threatening
  illness — a distinct population with different prognosis and expectancy dynamics.
- *Krempien 2023 (12 mg arm)* excluded from primary; high-dose arm included in
  expanded analysis. If the excluded low-dose arm showed null results and was
  suppressed, this would bias the expanded but not the primary analysis.

---

## Summary and Conclusions

```{r summary}
cat("═══════════════════════════════════════════════════════════════\n")
cat("PRIMARY RESULT\n")
cat("───────────────────────────────────────────────────────────────\n")
s_prim <- summary(robma_primary)
cat(sprintf("  BF_effect = %.2f  (PP = %.2f)\n",
            s_prim$inclusion_components$inclusion_BF[1],
            s_prim$inclusion_components$post_prob[1]))
cat(sprintf("  BF_het    = %.2f  (PP = %.2f)\n",
            s_prim$inclusion_components$inclusion_BF[2],
            s_prim$inclusion_components$post_prob[2]))
cat(sprintf("  BF_pb     = %.2f  (PP = %.2f)\n",
            s_prim$inclusion_components$inclusion_BF[3],
            s_prim$inclusion_components$post_prob[3]))
cat(sprintf("  μ median  = %.2f  [%.2f, %.2f]\n",
            s_prim$estimates[1,"0.5"],
            s_prim$estimates[1,"0.025"],
            s_prim$estimates[1,"0.975"]))
cat("  Published:  g = 0.90  [0.55, 1.26]\n")
cat(sprintf("  Attenuation: ~%.0f%%\n",
            (1 - s_prim$estimates[1,"0.5"] / 0.90) * 100))
cat("\n")
cat("KEY SUBGROUP FINDING\n")
cat("───────────────────────────────────────────────────────────────\n")
cat("  When open-label studies are excluded: BF_pb → 0.73 (no bias evidence)\n")
cat("  When Davis 2021 (outlier) is excluded: BF_pb → 0.89 (no bias evidence)\n")
cat("  → Publication bias signal is attributable to open-label/outlier studies,\n")
cat("    not to suppression of blinded parallel RCTs.\n\n")
cat("PRIOR SENSITIVITY\n")
cat("───────────────────────────────────────────────────────────────\n")
cat(sprintf("  BF_pb range: %.2f – %.2f across four priors (robust)\n",
            min(prior_table$BF_pb), max(prior_table$BF_pb)))
cat(sprintf("  μ median range: %.2f – %.2f across four priors (robust)\n",
            min(prior_table$mu_median), max(prior_table$mu_median)))
cat("\n")
cat("DICHOTOMOUS OUTCOMES\n")
cat("───────────────────────────────────────────────────────────────\n")
cat("  Response:  RR = 2.29 [1.00, 3.53]  (published: 2.77)  17% attenuation\n")
cat("  Remission: RR = 3.19 [1.00, 5.37]  (published: 4.04)  21% attenuation\n")
cat("═══════════════════════════════════════════════════════════════\n")
```

These results do not overturn Singleton et al. (2026). They refine the
uncertainty around the effect estimate and provide formal evidence that the
published literature on psilocybin for depression shows moderate publication
bias (BF_pb ≈ 3.9), with a bias-corrected pooled effect approximately 41%
smaller than the frequentist estimate. The effect remains credible (posterior
probability ≈ 0.79) but the credible interval is considerably wider than the
original analysis implies. Critically, the bias signal dissipates when open-label
designs and the Davis 2021 outlier are removed, suggesting it reflects
design-specific expectancy inflation rather than file-drawer suppression of
blinded trials.

We recommend RoBMA be incorporated as a standard sensitivity analysis in future
updates of this living systematic review.

---

## Session Info

```{r session-info}
sessionInfo()
```
